---
title: "Figure_S17"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## **📌 Load Required Libraries**
```{r load_libraries, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse) 
library(ggfortify)
library(ggplot2)
library(cluster)
library(edgeR)
library(limma)
library(Homo.sapiens)
library(BiocParallel)
library(qvalue)
library(pheatmap)
library(clusterProfiler)
library(AnnotationDbi)
library(org.Hs.eg.db)
library(RColorBrewer)
library(readr)
library(TxDb.Hsapiens.UCSC.hg38.knownGene)
library(DOSE)

# Load UCSC transcript database
txdb <- TxDb.Hsapiens.UCSC.hg38.knownGene
```

## **📌 0.1 Micromolar**
## **📌 Read and Process Data**
```{r load_DEGs, echo=TRUE, results='hide', message=FALSE, warning=FALSE}
# Load the saved datasets
prob_1_0.1 <- read.csv("data/prob_1_0.1.csv")$Entrez_ID
prob_2_0.1 <- read.csv("data/prob_2_0.1.csv")$Entrez_ID
prob_3_0.1 <- read.csv("data/prob_3_0.1.csv")$Entrez_ID
prob_1_0.5 <- read.csv("data/prob_1_0.5.csv")$Entrez_ID
prob_2_0.5 <- read.csv("data/prob_2_0.5.csv")$Entrez_ID
prob_3_0.5 <- read.csv("data/prob_3_0.5.csv")$Entrez_ID
prob_4_0.5 <- read.csv("data/prob_4_0.5.csv")$Entrez_ID
prob_5_0.5 <- read.csv("data/prob_5_0.5.csv")$Entrez_ID


CX_0.1_3 <- read.csv("data/DEGs/Toptable_CX_0.1_3.csv")
background<-as.character(CX_0.1_3$Entrez_ID)
```

## **📌 Non response (0.1 µM)**
## **📌 GO Enrichment Clusterprofiler**
```{r GO1, echo=TRUE, message=FALSE, fig.width=12, fig.height=12}
# 📦 Load Libraries
library(tidyverse)
library(patchwork)
library(data.table)

# 📁 Load File
go_df <- fread("data/BP/CorMotif_Terms_Combined/GO_All_Non_response_(0.1).csv")

# 🧠 Convert and filter (only adj p < 0.05)
process_enrichment_tibble <- function(df, ontology, category_label) {
  df %>%
    filter(Ontology == ontology & p.adjust < 0.05) %>%
    mutate(neglog = -log(p.adjust)) %>%
    arrange(desc(neglog)) %>%
    slice(1:20) %>%
    mutate(Category = category_label)
}

# Create tibbles for each GO class
BP_Tibble <- process_enrichment_tibble(go_df, "BP", "Biological Process")
MF_Tibble <- process_enrichment_tibble(go_df, "MF", "Molecular Function")
CC_Tibble <- process_enrichment_tibble(go_df, "CC", "Cellular Component")

# 📊 Plot function
process_enrichment_plot <- function(tibble, title, color) {
  ggplot(tibble, aes(x = neglog, y = reorder(Description, neglog))) +
    geom_bar(stat = "identity", fill = color) +
    labs(
      x = "-log(p-adjust)", y = title,
      title = paste("Top 20", title, "GO Terms (adj p < 0.05)")
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(size = 12, face = "bold", colour = "black", angle = 45, hjust = 1),
      axis.text.y = element_text(size = 12, face = "bold", colour = "black"),
      axis.title.x = element_text(size = 14, face = "bold", colour = "black"),
      axis.title.y = element_text(size = 14, face = "bold", colour = "black"),
      plot.title = element_text(size = 14, face = "bold", colour = "black"),
      panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.3)
    ) +
    xlim(0, max(tibble$neglog, na.rm = TRUE) + 1)
}

# 🔧 Plot for each GO category
plot_BP <- process_enrichment_plot(BP_Tibble, "Biological Process", "#2E86C1")
#plot_MF <- process_enrichment_plot(MF_Tibble, "Molecular Function", "#28B463")
#plot_CC <- process_enrichment_plot(CC_Tibble, "Cellular Component", "#D35400")

# 🧩 Combine plots
combined_plot <- plot_BP
combined_plot
```

## **📌 CX_DOX_1**
## **📌 GO Enrichment Clusterprofiler**
```{r GO2, echo=TRUE, message=FALSE, fig.width=12, fig.height=12}
# 📦 Load Libraries
library(tidyverse)
library(data.table)
library(patchwork)

# 📁 Load GO CSV for CX-DOX mid-late response (0.1)
go_df <- fread("data/BP/CorMotif_Terms_Combined/GO_All_CX-DOX_mid-late_response_(0.1).csv")

# 🧠 Convert and filter (only adj p < 0.05)
process_enrichment_tibble <- function(df, ontology, category_label) {
  df %>%
    filter(Ontology == ontology & p.adjust < 0.05) %>%
    mutate(neglog = -log(p.adjust)) %>%
    arrange(desc(neglog)) %>%
    slice(1:20) %>%
    mutate(Category = category_label)
}

# Create tibbles for each GO class
BP_Tibble <- process_enrichment_tibble(go_df, "BP", "Biological Process")
MF_Tibble <- process_enrichment_tibble(go_df, "MF", "Molecular Function")
CC_Tibble <- process_enrichment_tibble(go_df, "CC", "Cellular Component")

# 📊 Plot function
process_enrichment_plot <- function(tibble, title, color) {
  ggplot(tibble, aes(x = neglog, y = reorder(Description, neglog))) +
    geom_bar(stat = "identity", fill = color) +
    labs(
      x = "-log(p-adjust)", y = title,
      title = paste("Top 20", title, "GO Terms (adj p < 0.05)")
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(size = 12, face = "bold", colour = "black", angle = 45, hjust = 1),
      axis.text.y = element_text(size = 12, face = "bold", colour = "black"),
      axis.title.x = element_text(size = 14, face = "bold", colour = "black"),
      axis.title.y = element_text(size = 14, face = "bold", colour = "black"),
      plot.title = element_text(size = 14, face = "bold", colour = "black"),
      panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.3)
    ) +
    xlim(0, max(tibble$neglog, na.rm = TRUE) + 1)
}

# 🔧 Plot for each GO category
plot_BP <- process_enrichment_plot(BP_Tibble, "Biological Process", "#2E86C1")
plot_MF <- process_enrichment_plot(MF_Tibble, "Molecular Function", "#28B463")
plot_CC <- process_enrichment_plot(CC_Tibble, "Cellular Component", "#D35400")

# 🧩 Combine plots
combined_plot <- plot_BP
combined_plot

```

## **📌 DOX_sp_1**
## **📌 GO Enrichment Clusterprofiler**
```{r GO3, echo=TRUE, message=FALSE, fig.width=12, fig.height=12}
# 📦 Load Required Libraries
library(tidyverse)
library(data.table)
library(patchwork)

# 📁 Load GO Enrichment CSV
go_df <- fread("data/BP/CorMotif_Terms_Combined/GO_All_DOX_only_mid-late_(0.1).csv")

# 🧠 Convert and filter (only adj p < 0.05)
process_enrichment_tibble <- function(df, ontology, category_label) {
  df %>%
    filter(Ontology == ontology & p.adjust < 0.05) %>%
    mutate(neglog = -log(p.adjust)) %>%
    arrange(desc(neglog)) %>%
    slice(1:20) %>%
    mutate(Category = category_label)
}

# Create tibbles for each GO class
BP_Tibble <- process_enrichment_tibble(go_df, "BP", "Biological Process")
MF_Tibble <- process_enrichment_tibble(go_df, "MF", "Molecular Function")
CC_Tibble <- process_enrichment_tibble(go_df, "CC", "Cellular Component")

# 📊 Plot function
process_enrichment_plot <- function(tibble, title, color) {
  ggplot(tibble, aes(x = neglog, y = reorder(Description, neglog))) +
    geom_bar(stat = "identity", fill = color) +
    labs(
      x = "-log(p-adjust)", y = title,
      title = paste("Top 20", title, "GO Terms (adj p < 0.05)")
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(size = 12, face = "bold", colour = "black", angle = 45, hjust = 1),
      axis.text.y = element_text(size = 12, face = "bold", colour = "black"),
      axis.title.x = element_text(size = 14, face = "bold", colour = "black"),
      axis.title.y = element_text(size = 14, face = "bold", colour = "black"),
      plot.title = element_text(size = 14, face = "bold", colour = "black"),
      panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.3)
    ) +
    xlim(0, max(tibble$neglog, na.rm = TRUE) + 1)
}

# 🔧 Plot for each GO category
plot_BP <- process_enrichment_plot(BP_Tibble, "Biological Process", "#2E86C1")
plot_MF <- process_enrichment_plot(MF_Tibble, "Molecular Function", "#28B463")
plot_CC <- process_enrichment_plot(CC_Tibble, "Cellular Component", "#D35400")

# 🧩 Combine plots
combined_plot <- plot_BP
combined_plot
```


## **📌 Non response (0.5 µM)**
## **📌 GO Enrichment Clusterprofiler**
```{r GO4, echo=TRUE, message=FALSE, fig.width=12, fig.height=12}
# 📦 Load Required Libraries
library(tidyverse)
library(data.table)
library(patchwork)

# 📁 Load Enrichment File
go_df <- fread("data/BP/CorMotif_Terms_Combined/GO_All_Non_response_(0.5).csv")

# 🧠 Process Enrichment (only adj p < 0.05)
process_enrichment_tibble <- function(df, ontology, category_label) {
  df %>%
    filter(Ontology == ontology & p.adjust < 0.05) %>%
    mutate(neglog = -log(p.adjust)) %>%
    arrange(desc(neglog)) %>%
    slice(1:20) %>%
    mutate(Category = category_label)
}

# ⛏️ Extract each GO class
BP_Tibble <- process_enrichment_tibble(go_df, "BP", "Biological Process")
MF_Tibble <- process_enrichment_tibble(go_df, "MF", "Molecular Function")
CC_Tibble <- process_enrichment_tibble(go_df, "CC", "Cellular Component")

# 📊 Plotting Function
process_enrichment_plot <- function(tibble, title, color) {
  ggplot(tibble, aes(x = neglog, y = reorder(Description, neglog))) +
    geom_bar(stat = "identity", fill = color) +
    labs(
      x = "-log(p-adjust)", y = title,
      title = paste("Top 20", title, "GO Terms (adj p < 0.05)")
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(size = 12, face = "bold", colour = "black", angle = 45, hjust = 1),
      axis.text.y = element_text(size = 12, face = "bold", colour = "black"),
      axis.title.x = element_text(size = 14, face = "bold", colour = "black"),
      axis.title.y = element_text(size = 14, face = "bold", colour = "black"),
      plot.title = element_text(size = 14, face = "bold", colour = "black"),
      panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.3)
    ) +
    xlim(0, max(tibble$neglog, na.rm = TRUE) + 1)
}

# 🎨 Generate GO Plots
plot_BP <- process_enrichment_plot(BP_Tibble, "Biological Process", "#2E86C1")
plot_MF <- process_enrichment_plot(MF_Tibble, "Molecular Function", "#28B463")
plot_CC <- process_enrichment_plot(CC_Tibble, "Cellular Component", "#D35400")

# 🧩 Combine & Show
combined_plot <- plot_BP
combined_plot
```

## **📌 DOX_sp_2**
## **📌 GO Enrichment Clusterprofiler**
```{r GO5, echo=TRUE, message=FALSE, fig.width=12, fig.height=12}
# 📦 Load Required Libraries
library(tidyverse)
library(data.table)
library(patchwork)

# 📁 Load Enrichment File
go_df <- fread("data/BP/CorMotif_Terms_Combined/GO_All_DOX_specific_response_(0.5).csv")

# 🧠 Process Enrichment (only adj p < 0.05)
process_enrichment_tibble <- function(df, ontology, category_label) {
  df %>%
    filter(Ontology == ontology & p.adjust < 0.05) %>%
    mutate(neglog = -log(p.adjust)) %>%
    arrange(desc(neglog)) %>%
    slice(1:20) %>%
    mutate(Category = category_label)
}

# ⛏️ Extract each GO class
BP_Tibble <- process_enrichment_tibble(go_df, "BP", "Biological Process")
MF_Tibble <- process_enrichment_tibble(go_df, "MF", "Molecular Function")
CC_Tibble <- process_enrichment_tibble(go_df, "CC", "Cellular Component")

# 📊 Plotting Function
process_enrichment_plot <- function(tibble, title, color) {
  ggplot(tibble, aes(x = neglog, y = reorder(Description, neglog))) +
    geom_bar(stat = "identity", fill = color) +
    labs(
      x = "-log(p-adjust)", y = title,
      title = paste("Top 20", title, "GO Terms (adj p < 0.05)")
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(size = 12, face = "bold", colour = "black", angle = 45, hjust = 1),
      axis.text.y = element_text(size = 12, face = "bold", colour = "black"),
      axis.title.x = element_text(size = 14, face = "bold", colour = "black"),
      axis.title.y = element_text(size = 14, face = "bold", colour = "black"),
      plot.title = element_text(size = 14, face = "bold", colour = "black"),
      panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.3)
    ) +
    xlim(0, max(tibble$neglog, na.rm = TRUE) + 1)
}

# 🎨 Generate GO Plots
plot_BP <- process_enrichment_plot(BP_Tibble, "Biological Process", "#2E86C1")
plot_MF <- process_enrichment_plot(MF_Tibble, "Molecular Function", "#28B463")
plot_CC <- process_enrichment_plot(CC_Tibble, "Cellular Component", "#D35400")

# 🧩 Combine & Show
combined_plot <- plot_BP
combined_plot
```

## **📌 DOX_sp_3**
## **📌 GO Enrichment Clusterprofiler**
```{r GO6, echo=TRUE, message=FALSE, fig.width=12, fig.height=12}
# 📦 Load Required Libraries
library(tidyverse)
library(data.table)
library(patchwork)

# 📁 Load Enrichment File
go_df <- fread("data/BP/CorMotif_Terms_Combined/GO_All_DOX_only_mid-late_response_(0.5).csv")

# 🧠 Process Enrichment (only adj p < 0.05)
process_enrichment_tibble <- function(df, ontology, category_label) {
  df %>%
    filter(Ontology == ontology & p.adjust < 0.05) %>%
    mutate(neglog = -log(p.adjust)) %>%
    arrange(desc(neglog)) %>%
    slice(1:20) %>%
    mutate(Category = category_label)
}

# ⛏️ Extract each GO class
BP_Tibble <- process_enrichment_tibble(go_df, "BP", "Biological Process")
MF_Tibble <- process_enrichment_tibble(go_df, "MF", "Molecular Function")
CC_Tibble <- process_enrichment_tibble(go_df, "CC", "Cellular Component")

# 📊 Plotting Function
process_enrichment_plot <- function(tibble, title, color) {
  ggplot(tibble, aes(x = neglog, y = reorder(Description, neglog))) +
    geom_bar(stat = "identity", fill = color) +
    labs(
      x = "-log(p-adjust)", y = title,
      title = paste("Top 20", title, "GO Terms (adj p < 0.05)")
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(size = 12, face = "bold", colour = "black", angle = 45, hjust = 1),
      axis.text.y = element_text(size = 12, face = "bold", colour = "black"),
      axis.title.x = element_text(size = 14, face = "bold", colour = "black"),
      axis.title.y = element_text(size = 14, face = "bold", colour = "black"),
      plot.title = element_text(size = 14, face = "bold", colour = "black"),
      panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.3)
    ) +
    xlim(0, max(tibble$neglog, na.rm = TRUE) + 1)
}

# 🎨 Generate GO Plots
plot_BP <- process_enrichment_plot(BP_Tibble, "Biological Process", "#2E86C1")
plot_MF <- process_enrichment_plot(MF_Tibble, "Molecular Function", "#28B463")
plot_CC <- process_enrichment_plot(CC_Tibble, "Cellular Component", "#D35400")

# 🧩 Combine & Show
combined_plot <- plot_BP
combined_plot
```

## **📌 CX_DOX_2**
## **📌 GO Enrichment Clusterprofiler**
```{r GO7, echo=TRUE, message=FALSE, fig.width=12, fig.height=12}
# 📦 Load Required Libraries
library(tidyverse)
library(data.table)
library(patchwork)

# 📁 Load Enrichment File
go_df <- fread("data/BP/CorMotif_Terms_Combined/GO_All_CX_total_+_DOX_early_response_(0.5).csv")

# 🧠 Process Enrichment (only adj p < 0.05)
process_enrichment_tibble <- function(df, ontology, category_label) {
  df %>%
    filter(Ontology == ontology & p.adjust < 0.05) %>%
    mutate(neglog = -log(p.adjust)) %>%
    arrange(desc(neglog)) %>%
    slice(1:20) %>%
    mutate(Category = category_label)
}

# ⛏️ Extract each GO class
BP_Tibble <- process_enrichment_tibble(go_df, "BP", "Biological Process")
MF_Tibble <- process_enrichment_tibble(go_df, "MF", "Molecular Function")
CC_Tibble <- process_enrichment_tibble(go_df, "CC", "Cellular Component")

# 📊 Plotting Function
process_enrichment_plot <- function(tibble, title, color) {
  ggplot(tibble, aes(x = neglog, y = reorder(Description, neglog))) +
    geom_bar(stat = "identity", fill = color) +
    labs(
      x = "-log(p-adjust)", y = title,
      title = paste("Top 20", title, "GO Terms (adj p < 0.05)")
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(size = 12, face = "bold", colour = "black", angle = 45, hjust = 1),
      axis.text.y = element_text(size = 12, face = "bold", colour = "black"),
      axis.title.x = element_text(size = 14, face = "bold", colour = "black"),
      axis.title.y = element_text(size = 14, face = "bold", colour = "black"),
      plot.title = element_text(size = 14, face = "bold", colour = "black"),
      panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.3)
    ) +
    xlim(0, max(tibble$neglog, na.rm = TRUE) + 1)
}

# 🎨 Generate GO Plots
plot_BP <- process_enrichment_plot(BP_Tibble, "Biological Process", "#2E86C1")
plot_MF <- process_enrichment_plot(MF_Tibble, "Molecular Function", "#28B463")
plot_CC <- process_enrichment_plot(CC_Tibble, "Cellular Component", "#D35400")

# 🧩 Combine & Show
combined_plot <- plot_BP
combined_plot
```

## **📌 CX_DOX_3**
## **📌 GO Enrichment Clusterprofiler**
```{r GO8, echo=TRUE, message=FALSE, fig.width=12, fig.height=12}
# 📦 Load Required Libraries
library(tidyverse)
library(data.table)
library(patchwork)

# 📁 Load Enrichment File
go_df <- fread("data/BP/CorMotif_Terms_Combined/GO_All_DOX_early_+_CX-DOX_mid-late_response_(0.5).csv")

# 🧠 Process Enrichment (only adj p < 0.05)
process_enrichment_tibble <- function(df, ontology, category_label) {
  df %>%
    filter(Ontology == ontology & p.adjust < 0.05) %>%
    mutate(neglog = -log(p.adjust)) %>%
    arrange(desc(neglog)) %>%
    slice(1:20) %>%
    mutate(Category = category_label)
}

# ⛏️ Extract each GO class
BP_Tibble <- process_enrichment_tibble(go_df, "BP", "Biological Process")
MF_Tibble <- process_enrichment_tibble(go_df, "MF", "Molecular Function")
CC_Tibble <- process_enrichment_tibble(go_df, "CC", "Cellular Component")

# 📊 Plotting Function
process_enrichment_plot <- function(tibble, title, color) {
  ggplot(tibble, aes(x = neglog, y = reorder(Description, neglog))) +
    geom_bar(stat = "identity", fill = color) +
    labs(
      x = "-log(p-adjust)", y = title,
      title = paste("Top 20", title, "GO Terms (adj p < 0.05)")
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(size = 12, face = "bold", colour = "black", angle = 45, hjust = 1),
      axis.text.y = element_text(size = 12, face = "bold", colour = "black"),
      axis.title.x = element_text(size = 14, face = "bold", colour = "black"),
      axis.title.y = element_text(size = 14, face = "bold", colour = "black"),
      plot.title = element_text(size = 14, face = "bold", colour = "black"),
      panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.3)
    ) +
    xlim(0, max(tibble$neglog, na.rm = TRUE) + 1)
}

# 🎨 Generate GO Plots
plot_BP <- process_enrichment_plot(BP_Tibble, "Biological Process", "#2E86C1")
plot_MF <- process_enrichment_plot(MF_Tibble, "Molecular Function", "#28B463")
plot_CC <- process_enrichment_plot(CC_Tibble, "Cellular Component", "#D35400")

# 🧩 Combine & Show
combined_plot <- plot_BP
combined_plot
```
