---
title: "Revision"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---
## **📌 Forest Plot: Heart Failure Risk Loci Enrichment**
```{r For_HF, echo=TRUE, message=FALSE, fig.height=10,fig.width=12}
# 📦 Load Required Libraries
# --- Libraries ---
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)

# --- Step 1: Heart Failure Risk Loci (Entrez IDs) ---
entrez_ids <- c(
  9709, 8882, 4023, 29959, 5496, 3992, 9415, 5308, 1026, 54437, 79068, 10221,
  9031, 1187, 1952, 3705, 84722, 7273, 23293, 155382, 9531, 602, 27258, 84163,
  81846, 79933, 56911, 64753, 93210, 1021, 283450, 5998, 57602, 114991, 7073,
  3156, 100101267, 22996, 285025, 11080, 11124, 54810, 7531, 27241, 4774, 57794,
  463, 91319, 6598, 9640, 2186, 26010, 80816, 571, 88, 51652, 64788, 90523, 2969,
  7781, 80777, 10725, 23387, 817, 134728, 8842, 949, 6934, 129787, 10327, 202052,
  2318, 5578, 6801, 6311, 10019, 80724, 217, 84909, 388591, 55101, 9839, 27161,
  5310, 387119, 4641, 5587, 55188, 222553, 9960, 22852, 10087, 9570, 54497,
  200942, 26249, 4137, 375056, 5409, 64116, 8291, 22876, 339855, 4864, 5142,
  221692, 55023, 51426, 6146, 84251, 8189, 27332, 57099, 1869, 1112, 23327,
  11264, 6001
)

# --- Step 2: Load DEG tables ---
deg_files <- list.files("data/DEGs/", pattern = "Toptable_.*\\.csv", full.names = TRUE)
deg_list  <- lapply(deg_files, read.csv)
names(deg_list) <- gsub("Toptable_|\\.csv", "", basename(deg_files))

# --- Step 3: Fisher test function (save raw counts to table) ---
fisher_or <- function(df, sample_name) {
  df <- df %>%
    mutate(
      DEG = adj.P.Val < 0.05,
      HF_risk = Entrez_ID %in% entrez_ids
    )

  a <- sum(df$DEG & df$HF_risk, na.rm = TRUE)
  b <- sum(df$DEG & !df$HF_risk, na.rm = TRUE)
  c <- sum(!df$DEG & df$HF_risk, na.rm = TRUE)
  d <- sum(!df$DEG & !df$HF_risk, na.rm = TRUE)

  test <- fisher.test(matrix(c(a, b, c, d), nrow = 2))

  tibble(
    Sample = sample_name,
    DE_Risk = a,
    DE_nonRisk = b,
    nonDE_Risk = c,
    nonDE_nonRisk = d,
    OR = unname(test$estimate),
    Lower_CI = test$conf.int[1],
    Upper_CI = test$conf.int[2],
    Pval = test$p.value,
    Stars = case_when(
      test$p.value < 0.001 ~ "***",
      test$p.value < 0.01  ~ "**",
      test$p.value < 0.05  ~ "*",
      TRUE ~ ""
    )
  )
}

# --- Step 4: Run Fisher tests for all DEG files ---
results <- bind_rows(mapply(fisher_or, deg_list, names(deg_list), SIMPLIFY = FALSE))

# --- Step 5: Extract metadata (Drug, Conc, Time) ---
results <- results %>%
  separate(Sample, into = c("Drug","Conc","Time"), sep = "_") %>%
  mutate(
    Label = paste(Drug, Conc, sep = "_"),
    Time = factor(Time, levels = c("3","24","48"))
  )

# --- Step 6: Forest plot (clean, like before) ---
ggplot(results, aes(x = Label, y = OR, ymin = Lower_CI, ymax = Upper_CI)) +
  geom_pointrange(aes(color = Pval < 0.05), size = 0.9) +
  geom_text(aes(label = Stars), hjust = -0.5, size = 5) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "grey40")) +
  coord_flip() +
  facet_wrap(~Time, ncol = 1, scales = "free_y") +
  ylim(0, 20) +
  labs(
    title = "Heart Failure Risk Loci Enrichment Across Conditions",
    x = "Condition (Drug_Conc)",
    y = "Odds Ratio (95% CI)"
  ) +
  theme_classic(base_size = 14) +
  theme(
    legend.position = "none",
    strip.text = element_text(face = "bold", size = 12)
  )

# --- Step 7: Export results with raw numbers for supplement ---
write.csv(results, "data/HF_Cardiotoxicity_ForestPlot_Data.csv", row.names = FALSE)
```


## **📌 Forest Plot: DOX Cardiotoxicity Loci Enrichment**
```{r For_DC, echo=TRUE, message=FALSE, fig.height=10,fig.width=12}
# --- Libraries ---
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)

# --- Step 1: Define DOX cardiotoxicity risk loci (Entrez IDs) ---
entrez_ids <- c(
  847, 873, 2064, 2878, 2944, 3038, 4846, 51196, 5880, 6687,
  7799, 4292, 5916, 3077, 51310, 9154, 64078, 5244, 10057, 10060,
  89845, 56853, 4625, 1573, 79890
)

# --- Step 2: Load DEG tables ---
deg_files <- list.files("data/DEGs/", pattern = "Toptable_.*\\.csv", full.names = TRUE)
deg_list  <- lapply(deg_files, read.csv)
names(deg_list) <- gsub("Toptable_|\\.csv", "", basename(deg_files))

# --- Step 3: Fisher test function (now saves raw counts too) ---
fisher_or <- function(df, sample_name) {
  df <- df %>%
    mutate(
      DEG = adj.P.Val < 0.05,
      DOXrisk = Entrez_ID %in% entrez_ids
    )

  a <- sum(df$DEG & df$DOXrisk, na.rm = TRUE)
  b <- sum(df$DEG & !df$DOXrisk, na.rm = TRUE)
  c <- sum(!df$DEG & df$DOXrisk, na.rm = TRUE)
  d <- sum(!df$DEG & !df$DOXrisk, na.rm = TRUE)

  test <- fisher.test(matrix(c(a, b, c, d), nrow = 2))

  tibble(
    Sample = sample_name,
    DE_Risk = a,
    DE_nonRisk = b,
    nonDE_Risk = c,
    nonDE_nonRisk = d,
    OR = unname(test$estimate),
    Lower_CI = test$conf.int[1],
    Upper_CI = test$conf.int[2],
    Pval = test$p.value,
    Stars = case_when(
      test$p.value < 0.001 ~ "***",
      test$p.value < 0.01  ~ "**",
      test$p.value < 0.05  ~ "*",
      TRUE ~ ""
    )
  )
}

# --- Step 4: Run Fisher tests for all DEG files ---
results <- bind_rows(mapply(fisher_or, deg_list, names(deg_list), SIMPLIFY = FALSE))

# --- Step 5: Extract metadata (Drug, Conc, Time) ---
results <- results %>%
  separate(Sample, into = c("Drug","Conc","Time"), sep = "_") %>%
  mutate(
    Label = paste(Drug, Conc, sep = "_"),
    Time = factor(Time, levels = c("3","24","48"))
  )

# --- Step 6: Forest plot (same clean look, 0–20 scale, stars only) ---
ggplot(results, aes(x = Label, y = OR, ymin = Lower_CI, ymax = Upper_CI)) +
  geom_pointrange(aes(color = Pval < 0.05), size = 0.9) +
  geom_text(aes(label = Stars), hjust = -0.5, size = 5) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "grey40")) +
  coord_flip() +
  facet_wrap(~Time, ncol = 1, scales = "free_y") +
  ylim(0, 20) +
  labs(
    title = "DOX Cardiotoxicity Loci Enrichment",
    x = "Condition (Drug_Conc)",
    y = "Odds Ratio (95% CI)"
  ) +
  theme_classic(base_size = 14) +
  theme(
    legend.position = "none",
    strip.text = element_text(face = "bold", size = 12)
  )

# --- Step 7: Save results with raw counts for supplement ---
write.csv(results, "data/DOX_Cardiotoxicity_ForestPlot_Data.csv", row.names = FALSE)
```

## **📌 Forest Plot: AC Cardiotoxicity Loci Enrichment**
```{r For_AC, echo=TRUE, message=FALSE, fig.height=10,fig.width=12}
# --- Libraries ---
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)

# --- Step 1: AC Cardiotoxicity Risk Loci (Entrez IDs) ---
Entrez_IDs <- c(
  6272, 8029, 11128, 79899, 54477, 121665, 5095, 22863, 57161, 4692,
  8214, 23151, 56606, 108, 22999, 56895, 9603, 3181, 4023, 10499,
  92949, 4363, 10057, 5243, 5244, 5880, 1535, 2950, 847, 5447,
  3038, 3077, 4846, 3958, 23327, 29899, 23155, 80856, 55020, 78996,
  23262, 150383, 9620, 79730, 344595, 5066, 6251, 3482, 9588, 339416,
  7292, 55157, 87769, 23409, 720, 3107, 54535, 1590, 80059, 7991,
  57110, 8803, 323, 54826, 5916, 23371, 283337, 64078, 80010, 1933,
  10818, 51020
)

# --- Step 2: Load DEG tables ---
deg_files <- list.files("data/DEGs/", pattern = "Toptable_.*\\.csv", full.names = TRUE)
deg_list  <- lapply(deg_files, read.csv)
names(deg_list) <- gsub("Toptable_|\\.csv", "", basename(deg_files))

# --- Step 3: Fisher test function (with raw counts) ---
fisher_or <- function(df, sample_name) {
  df <- df %>%
    mutate(
      DEG = adj.P.Val < 0.05,
      AC_risk = Entrez_ID %in% Entrez_IDs
    )

  a <- sum(df$DEG & df$AC_risk, na.rm = TRUE)
  b <- sum(df$DEG & !df$AC_risk, na.rm = TRUE)
  c <- sum(!df$DEG & df$AC_risk, na.rm = TRUE)
  d <- sum(!df$DEG & !df$AC_risk, na.rm = TRUE)

  test <- fisher.test(matrix(c(a, b, c, d), nrow = 2))

  tibble(
    Sample = sample_name,
    DE_Risk = a,
    DE_nonRisk = b,
    nonDE_Risk = c,
    nonDE_nonRisk = d,
    OR = unname(test$estimate),
    Lower_CI = test$conf.int[1],
    Upper_CI = test$conf.int[2],
    Pval = test$p.value,
    Stars = case_when(
      test$p.value < 0.001 ~ "***",
      test$p.value < 0.01  ~ "**",
      test$p.value < 0.05  ~ "*",
      TRUE ~ ""
    )
  )
}

# --- Step 4: Run Fisher tests for all DEG files ---
results <- bind_rows(mapply(fisher_or, deg_list, names(deg_list), SIMPLIFY = FALSE))

# --- Step 5: Extract metadata (Drug, Conc, Time) ---
results <- results %>%
  separate(Sample, into = c("Drug","Conc","Time"), sep = "_") %>%
  mutate(
    Label = paste(Drug, Conc, sep = "_"),
    Time = factor(Time, levels = c("3","24","48"))
  )

# --- Step 6: Forest plot (scale 0–20, faceted by Time) ---
ggplot(results, aes(x = Label, y = OR, ymin = Lower_CI, ymax = Upper_CI)) +
  geom_pointrange(aes(color = Pval < 0.05), size = 0.9) +
  geom_text(aes(label = Stars), hjust = -0.5, size = 5) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "grey40")) +
  coord_flip() +
  facet_wrap(~Time, ncol = 1, scales = "free_y") +
  ylim(0, 20) +
  labs(
    title = "AC Cardiotoxicity Loci Enrichment Across Conditions",
    x = "Condition (Drug_Conc)",
    y = "Odds Ratio (95% CI)"
  ) +
  theme_classic(base_size = 14) +
  theme(
    legend.position = "none",
    strip.text = element_text(face = "bold", size = 12)
  )

# --- Step 7: Export results table (with raw numbers + OR) ---
write.csv(results, "data/AC_Cardiotoxicity_ForestPlot_Data.csv", row.names = FALSE)
```

## **📌 Odds Ratios for CorrMotif Groups (Heart-specific genes)**
```{r For_corHS, echo=TRUE, message=FALSE, fig.height=10,fig.width=12}
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
library(org.Hs.eg.db)
library(AnnotationDbi)

# --- Load Heart-Specific Genes ---
heart_genes <- read.csv("data/Human_Heart_Genes.csv", stringsAsFactors = FALSE)
heart_genes$Entrez_ID <- mapIds(
  org.Hs.eg.db,
  keys = heart_genes$Gene,
  column = "ENTREZID",
  keytype = "SYMBOL",
  multiVals = "first"
)
heart_entrez_ids <- na.omit(heart_genes$Entrez_ID)

# --- Load CorrMotif Groups ---
# 0.1 µM
prob_1_0.1 <- as.character(read.csv("data/prob_1_0.1.csv")$Entrez_ID)
prob_2_0.1 <- as.character(read.csv("data/prob_2_0.1.csv")$Entrez_ID)
prob_3_0.1 <- as.character(read.csv("data/prob_3_0.1.csv")$Entrez_ID)

# 0.5 µM
prob_1_0.5 <- as.character(read.csv("data/prob_1_0.5.csv")$Entrez_ID)
prob_2_0.5 <- as.character(read.csv("data/prob_2_0.5.csv")$Entrez_ID)
prob_3_0.5 <- as.character(read.csv("data/prob_3_0.5.csv")$Entrez_ID)
prob_4_0.5 <- as.character(read.csv("data/prob_4_0.5.csv")$Entrez_ID)
prob_5_0.5 <- as.character(read.csv("data/prob_5_0.5.csv")$Entrez_ID)

# --- Annotate Groups ---
df_0.1 <- data.frame(Entrez_ID = unique(c(prob_1_0.1, prob_2_0.1, prob_3_0.1))) %>%
  mutate(
    Response_Group = case_when(
      Entrez_ID %in% prob_1_0.1 ~ "Non response (0.1)",
      Entrez_ID %in% prob_2_0.1 ~ "CX_DOX_1",
      Entrez_ID %in% prob_3_0.1 ~ "DOX_sp_1"
    ),
    Category = ifelse(Entrez_ID %in% heart_entrez_ids,
                      "Heart-specific Genes", "Non-Heart-specific Genes"),
    Concentration = "0.1"
  )

df_0.5 <- data.frame(Entrez_ID = unique(c(prob_1_0.5, prob_2_0.5, prob_3_0.5, prob_4_0.5, prob_5_0.5))) %>%
  mutate(
    Response_Group = case_when(
      Entrez_ID %in% prob_1_0.5 ~ "Non response (0.5)",
      Entrez_ID %in% prob_2_0.5 ~ "DOX_sp_2",
      Entrez_ID %in% prob_3_0.5 ~ "DOX_sp_3",
      Entrez_ID %in% prob_4_0.5 ~ "CX_DOX_2",
      Entrez_ID %in% prob_5_0.5 ~ "CX_DOX_3"
    ),
    Category = ifelse(Entrez_ID %in% heart_entrez_ids,
                      "Heart-specific Genes", "Non-Heart-specific Genes"),
    Concentration = "0.5"
  )

df_combined <- bind_rows(df_0.1, df_0.5)

# --- Fisher Odds Ratio Function ---
fisher_or_group <- function(df_group, df_all, group_name, conc) {
  # counts in group
  a <- sum(df_group$Category == "Heart-specific Genes")
  b <- sum(df_group$Category == "Non-Heart-specific Genes")

  # counts in rest of groups at same conc
  ref <- df_all %>% filter(Response_Group != group_name)
  c <- sum(ref$Category == "Heart-specific Genes")
  d <- sum(ref$Category == "Non-Heart-specific Genes")

  mat <- matrix(c(a, b, c, d), nrow = 2)
  if (any(mat == 0)) mat <- mat + 0.5  # continuity correction

  test <- fisher.test(mat)

  tibble(
    Response_Group = group_name,
    Concentration  = conc,
    a = a, b = b, c = c, d = d,
    OR = unname(test$estimate),
    Lower_CI = test$conf.int[1],
    Upper_CI = test$conf.int[2],
    Pval = test$p.value,
    Stars = case_when(
      test$p.value < 0.001 ~ "***",
      test$p.value < 0.01  ~ "**",
      test$p.value < 0.05  ~ "*",
      TRUE ~ ""
    )
  )
}

# --- Run Fisher tests safely ---
results <- list()
for (conc in unique(df_combined$Concentration)) {
  conc_df <- df_combined %>% filter(Concentration == conc)
  for (grp in unique(conc_df$Response_Group)) {
    grp_df <- conc_df %>% filter(Response_Group == grp)
    results[[paste(conc, grp)]] <- fisher_or_group(grp_df, conc_df, grp, conc)
  }
}
results <- bind_rows(results)

# --- Save Results Table ---
write.csv(results, "data/CorrMotif_HeartGenes_OddsRatios.csv", row.names = FALSE)

# --- Forest Plot ---
ggplot(results, aes(x = Response_Group, y = OR, ymin = Lower_CI, ymax = Upper_CI)) +
  geom_pointrange(aes(color = Pval < 0.05), size = 0.9) +
  geom_text(aes(label = Stars), hjust = -0.5, size = 5) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "grey40")) +
  coord_flip() +
  facet_wrap(~Concentration, ncol = 1, scales = "free_y") +  # facet by concentration instead of time
  ylim(0, 20) +
  labs(
    title = "Heart-Specific Gene Enrichment Across CorrMotif Groups",
    x = "Response Group",
    y = "Odds Ratio (95% CI)"
  ) +
  theme_classic(base_size = 14) +
  theme(
    legend.position = "none",
    strip.text = element_text(face = "bold", size = 12)
  )
```


## **📌 Scatter Plot: DOX vs VEH vs CX vs VEH Condition: 24 hr, 0.5 µM**
```{r SC_1, echo=TRUE, message=FALSE, fig.height=6,fig.width=8}
library(ggplot2)

# --- Load Data ---
CX_0.5_24 <- read.csv("data/DEGs/Toptable_CX_0.5_24.csv")
DOX_0.5_24 <- read.csv("data/DEGs/Toptable_DOX_0.5_24.csv")

# --- Ensure Entrez_ID is character ---
CX_0.5_24$Entrez_ID <- as.character(CX_0.5_24$Entrez_ID)
DOX_0.5_24$Entrez_ID <- as.character(DOX_0.5_24$Entrez_ID)

# --- Merge on Entrez_ID ---
merged_24h_0.5 <- merge(
  CX_0.5_24, DOX_0.5_24,
  by = "Entrez_ID", suffixes = c("_CX", "_DOX")
)

# --- Correlation ---
cor_test <- cor.test(
  merged_24h_0.5$logFC_CX,
  merged_24h_0.5$logFC_DOX,
  method = "pearson"
)

r_val <- round(cor_test$estimate, 3)
p_val <- formatC(cor_test$p.value, format = "e", digits = 2)  # scientific notation
label_text <- paste0("r = ", r_val, "\n", "p = ", p_val)

# --- Scatter Plot with fixed label placement ---
ggplot(merged_24h_0.5, aes(x = logFC_CX, y = logFC_DOX)) +
  geom_point(alpha = 0.5, color = "black") +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  labs(
    title = "CX vs DOX logFC (24 hr, 0.5 µM)",
    x = "logFC (CX vs VEH)",
    y = "logFC (DOX vs VEH)"
  ) +
  theme_minimal(base_size = 14) +
  annotate(
    "text",
    x = -Inf, y = Inf, hjust = -0.1, vjust = 1.2,  # top-left corner inside panel
    label = label_text,
    size = 5, fontface = "bold"
  )
```

## **📌 Scatter Plot: DOX vs VEH vs CX vs VEH Condition: 48 hr, 0.5 µM**
```{r SC_2, echo=TRUE, message=FALSE, fig.height=6,fig.width=8}
library(ggplot2)

# --- Load Data ---
CX_0.5_48 <- read.csv("data/DEGs/Toptable_CX_0.5_48.csv")
DOX_0.5_48 <- read.csv("data/DEGs/Toptable_DOX_0.5_48.csv")

# --- Ensure Entrez_ID is character ---
CX_0.5_48$Entrez_ID <- as.character(CX_0.5_48$Entrez_ID)
DOX_0.5_48$Entrez_ID <- as.character(DOX_0.5_48$Entrez_ID)

# --- Merge on Entrez_ID ---
merged_48h_0.5 <- merge(
  CX_0.5_48, DOX_0.5_48,
  by = "Entrez_ID", suffixes = c("_CX", "_DOX")
)


# --- Correlation ---
cor_test <- cor.test(
  merged_48h_0.5$logFC_CX,
  merged_48h_0.5$logFC_DOX,
  method = "pearson"
)

r_val <- round(cor_test$estimate, 3)
p_val <- formatC(cor_test$p.value, format = "e", digits = 2)  # scientific notation
label_text <- paste0("r = ", r_val, "\n", "p = ", p_val)

# --- Scatter Plot with fixed label placement ---
ggplot(merged_48h_0.5, aes(x = logFC_CX, y = logFC_DOX)) +
  geom_point(alpha = 0.5, color = "black") +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  labs(
    title = "CX vs DOX logFC (48 hr, 0.5 µM)",
    x = "logFC (CX vs VEH)",
    y = "logFC (DOX vs VEH)"
  ) +
  theme_minimal(base_size = 14) +
  annotate(
    "text",
    x = -Inf, y = Inf, hjust = -0.1, vjust = 1.2,  # top-left corner inside panel
    label = label_text,
    size = 5, fontface = "bold"
  )
```

## **📌 Scatter Plot: DOX vs VEH vs CX vs VEH Condition: 24 hr, 0.5 µM (DOX DEGs only)**
```{r SC_3, echo=TRUE, message=FALSE, fig.height=6,fig.width=8}
library(ggplot2)

# --- Load Data ---
CX_0.5_24 <- read.csv("data/DEGs/Toptable_CX_0.5_24.csv")
DOX_0.5_24 <- read.csv("data/DEGs/Toptable_DOX_0.5_24.csv")

# --- Ensure Entrez_ID is character ---
CX_0.5_24$Entrez_ID <- as.character(CX_0.5_24$Entrez_ID)
DOX_0.5_24$Entrez_ID <- as.character(DOX_0.5_24$Entrez_ID)

# --- Extract DEGs from DOX (adj.P.Val < 0.05) ---
dox_degs <- DOX_0.5_24$Entrez_ID[DOX_0.5_24$adj.P.Val < 0.05]

# --- Merge CX & DOX, filter for DOX DEGs only ---
merged_24h_0.5 <- merge(
  CX_0.5_24, DOX_0.5_24,
  by = "Entrez_ID", suffixes = c("_CX", "_DOX")
)

merged_24h_0.5 <- merged_24h_0.5[merged_24h_0.5$Entrez_ID %in% dox_degs, ]

# --- Correlation ---
cor_test <- cor.test(
  merged_24h_0.5$logFC_CX,
  merged_24h_0.5$logFC_DOX,
  method = "pearson"
)

r_val <- round(cor_test$estimate, 3)
p_val <- formatC(cor_test$p.value, format = "e", digits = 2)
label_text <- paste0("r = ", r_val, "\n", "p = ", p_val)

# --- Scatter Plot ---
ggplot(merged_24h_0.5, aes(x = logFC_CX, y = logFC_DOX)) +
  geom_point(alpha = 0.6, color = "black") +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  labs(
    title = "CX vs DOX logFC (24 hr, 0.5 µM, DOX DEGs only)",
    x = "logFC (CX vs VEH)",
    y = "logFC (DOX vs VEH)"
  ) +
  theme_minimal(base_size = 14) +
  annotate(
    "text",
    x = -Inf, y = Inf,
    hjust = -0.1, vjust = 1.2,
    label = label_text,
    size = 5, fontface = "bold"
  )

```


## **📌 Scatter Plot: DOX vs VEH vs CX vs VEH Condition: 48 hr, 0.5 µM (DOX DEGs only)**
```{r SC_4, echo=TRUE, message=FALSE, fig.height=6,fig.width=8}
library(ggplot2)

# --- Load Data ---
CX_0.5_48 <- read.csv("data/DEGs/Toptable_CX_0.5_48.csv")
DOX_0.5_48 <- read.csv("data/DEGs/Toptable_DOX_0.5_48.csv")

# --- Ensure Entrez_ID is character ---
CX_0.5_48$Entrez_ID <- as.character(CX_0.5_48$Entrez_ID)
DOX_0.5_48$Entrez_ID <- as.character(DOX_0.5_48$Entrez_ID)

# --- Extract DEGs from DOX (adj.P.Val < 0.05) ---
dox_degs <- DOX_0.5_48$Entrez_ID[DOX_0.5_48$adj.P.Val < 0.05]

# --- Merge CX & DOX, filter for DOX DEGs only ---
merged_48h_0.5 <- merge(
  CX_0.5_48, DOX_0.5_48,
  by = "Entrez_ID", suffixes = c("_CX", "_DOX")
)

merged_48h_0.5 <- merged_48h_0.5[merged_48h_0.5$Entrez_ID %in% dox_degs, ]

# --- Correlation ---
cor_test <- cor.test(
  merged_48h_0.5$logFC_CX,
  merged_48h_0.5$logFC_DOX,
  method = "pearson"
)

r_val <- round(cor_test$estimate, 3)
p_val <- formatC(cor_test$p.value, format = "e", digits = 2)
label_text <- paste0("r = ", r_val, "\n", "p = ", p_val)

# --- Scatter Plot ---
ggplot(merged_48h_0.5, aes(x = logFC_CX, y = logFC_DOX)) +
  geom_point(alpha = 0.6, color = "black") +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  labs(
    title = "CX vs DOX logFC (48 hr, 0.5 µM, DOX DEGs only)",
    x = "logFC (CX vs VEH)",
    y = "logFC (DOX vs VEH)"
  ) +
  theme_minimal(base_size = 14) +
  annotate(
    "text",
    x = -Inf, y = Inf,
    hjust = -0.1, vjust = 1.2,
    label = label_text,
    size = 5, fontface = "bold"
  )
```

## **📌 Scatter Plot: DOX vs VEH vs CX vs VEH Condition: 24 hr, 0.5 µM (DDR genes only, cleaned set)**
```{r SC_5, echo=TRUE, message=FALSE, fig.height=6,fig.width=8}
library(ggplot2)
library(dplyr)

# --- DDR gene set ---
entrez_ids <- c(
  10111, 1017, 1019, 1020, 1021, 1026, 1027, 10912, 11011, 1111,
  11200, 1385, 1643, 1647, 1869, 207, 2177, 25, 27113, 27244,
  3014, 317, 355, 4193, 4292, 4361, 4609, 4616, 4683, 472, 50484,
  5366, 5371, 54205, 545, 55367, 5591, 581, 5810, 5883, 5884,
  5888, 5893, 5925, 595, 5981, 6118, 637, 672, 7157, 7799,
  8243, 836, 841, 84126, 842, 8795, 891, 894, 896, 898,
  9133, 9134, 983, 9874, 993, 995, 5916
) %>% as.character()

# --- Load Data ---
CX_0.5_24 <- read.csv("data/DEGs/Toptable_CX_0.5_24.csv")
DOX_0.5_24 <- read.csv("data/DEGs/Toptable_DOX_0.5_24.csv")

CX_0.5_24$Entrez_ID <- as.character(CX_0.5_24$Entrez_ID)
DOX_0.5_24$Entrez_ID <- as.character(DOX_0.5_24$Entrez_ID)

# --- Merge and filter for DDR genes ---
merged_ddr_24h_0.5 <- merge(
  CX_0.5_24, DOX_0.5_24,
  by = "Entrez_ID", suffixes = c("_CX", "_DOX")
)

merged_ddr_24h_0.5 <- merged_ddr_24h_0.5 %>%
  filter(Entrez_ID %in% entrez_ids)

# --- Correlation ---
cor_test <- cor.test(
  merged_ddr_24h_0.5$logFC_CX,
  merged_ddr_24h_0.5$logFC_DOX,
  method = "pearson"
)

r_val <- round(cor_test$estimate, 3)
p_val <- formatC(cor_test$p.value, format = "e", digits = 2)
label_text <- paste0("r = ", r_val, "\n", "p = ", p_val)

# --- Scatter Plot ---
ggplot(merged_ddr_24h_0.5, aes(x = logFC_CX, y = logFC_DOX)) +
  geom_point(alpha = 0.8, color = "black") +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  labs(
    title = "CX vs DOX logFC (24 hr, 0.5 µM, DDR genes only)",
    x = "logFC (CX vs VEH)",
    y = "logFC (DOX vs VEH)"
  ) +
  theme_minimal(base_size = 14) +
  annotate(
    "text",
    x = -Inf, y = Inf,
    hjust = -0.1, vjust = 1.2,
    label = label_text,
    size = 5, fontface = "bold"
  )
```


## **📌 Scatter Plot: DOX vs VEH vs CX vs VEH Condition: 48 hr, 0.5 µM (DDR genes only)**

```{r SC_6, echo=TRUE, message=FALSE, fig.height=6,fig.width=8}
library(ggplot2)
library(dplyr)

# --- DDR gene set (Entrez IDs) ---
entrez_ids <- c(
  10111, 1017, 1019, 1020, 1021, 1026, 1027, 10912, 11011, 1111,
  11200, 1385, 1643, 1647, 1869, 207, 2177, 25, 27113, 27244,
  3014, 317, 355, 4193, 4292, 4361, 4609, 4616, 4683, 472, 50484,
  5366, 5371, 54205, 545, 55367, 5591, 581, 5810, 5883, 5884,
  5888, 5893, 5925, 595, 5981, 6118, 637, 672, 7157, 7799,
  8243, 836, 841, 84126, 842, 8795, 891, 894, 896, 898,
  9133, 9134, 983, 9874, 993, 995, 5916
) %>% as.character()

# --- Load Data ---
CX_0.5_48 <- read.csv("data/DEGs/Toptable_CX_0.5_48.csv")
DOX_0.5_48 <- read.csv("data/DEGs/Toptable_DOX_0.5_48.csv")

CX_0.5_48$Entrez_ID <- as.character(CX_0.5_48$Entrez_ID)
DOX_0.5_48$Entrez_ID <- as.character(DOX_0.5_48$Entrez_ID)

# --- Merge and filter for DDR genes ---
merged_ddr_48h_0.5 <- merge(
  CX_0.5_48, DOX_0.5_48,
  by = "Entrez_ID", suffixes = c("_CX", "_DOX")
)

merged_ddr_48h_0.5 <- merged_ddr_48h_0.5 %>%
  filter(Entrez_ID %in% entrez_ids)

# --- Correlation ---
cor_test <- cor.test(
  merged_ddr_48h_0.5$logFC_CX,
  merged_ddr_48h_0.5$logFC_DOX,
  method = "pearson"
)

r_val <- round(cor_test$estimate, 3)
p_val <- formatC(cor_test$p.value, format = "e", digits = 2)
label_text <- paste0("r = ", r_val, "\n", "p = ", p_val)

# --- Scatter Plot ---
ggplot(merged_ddr_48h_0.5, aes(x = logFC_CX, y = logFC_DOX)) +
  geom_point(alpha = 0.8, color = "black") +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  labs(
    title = "CX vs DOX logFC (48 hr, 0.5 µM, DDR genes only)",
    x = "logFC (CX vs VEH)",
    y = "logFC (DOX vs VEH)"
  ) +
  theme_minimal(base_size = 14) +
  annotate(
    "text",
    x = -Inf, y = Inf,
    hjust = -0.1, vjust = 1.2,
    label = label_text,
    size = 5, fontface = "bold"
  )
```

## **📌 Scatter Plot: DOX vs VEH vs CX vs VEH Condition: 24 hr, 0.5 µM (Heart-specific genes only)**

```{r SC_7, echo=TRUE, message=FALSE, fig.height=6,fig.width=8}
library(dplyr)
library(ggplot2)
library(org.Hs.eg.db)
library(AnnotationDbi)

# --- Load Heart-Specific Genes ---
heart_genes <- read.csv("data/Human_Heart_Genes.csv", stringsAsFactors = FALSE)
heart_genes$Entrez_ID <- mapIds(
  org.Hs.eg.db,
  keys = heart_genes$Gene,
  column = "ENTREZID",
  keytype = "SYMBOL",
  multiVals = "first"
)
heart_entrez_ids <- na.omit(heart_genes$Entrez_ID) %>% as.character()

# --- Load DEG Data ---
CX_0.5_24 <- read.csv("data/DEGs/Toptable_CX_0.5_24.csv")
DOX_0.5_24 <- read.csv("data/DEGs/Toptable_DOX_0.5_24.csv")

CX_0.5_24$Entrez_ID <- as.character(CX_0.5_24$Entrez_ID)
DOX_0.5_24$Entrez_ID <- as.character(DOX_0.5_24$Entrez_ID)

# --- Merge and filter for heart-specific genes ---
merged_heart_24h_0.5 <- merge(
  CX_0.5_24, DOX_0.5_24,
  by = "Entrez_ID", suffixes = c("_CX", "_DOX")
)

merged_heart_24h_0.5 <- merged_heart_24h_0.5 %>%
  filter(Entrez_ID %in% heart_entrez_ids)

# --- Correlation ---
cor_test <- cor.test(
  merged_heart_24h_0.5$logFC_CX,
  merged_heart_24h_0.5$logFC_DOX,
  method = "pearson"
)

r_val <- round(cor_test$estimate, 3)
p_val <- formatC(cor_test$p.value, format = "e", digits = 2)
label_text <- paste0("r = ", r_val, "\n", "p = ", p_val)

# --- Scatter Plot ---
ggplot(merged_heart_24h_0.5, aes(x = logFC_CX, y = logFC_DOX)) +
  geom_point(alpha = 0.8, color = "black") +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  labs(
    title = "CX vs DOX logFC (24 hr, 0.5 µM, Heart-specific genes only)",
    x = "logFC (CX vs VEH)",
    y = "logFC (DOX vs VEH)"
  ) +
  theme_minimal(base_size = 14) +
  annotate(
    "text",
    x = -Inf, y = Inf,
    hjust = -0.1, vjust = 1.2,
    label = label_text,
    size = 5, fontface = "bold"
  )
```

## **📌 Scatter Plot: DOX vs VEH vs CX vs VEH Condition: 48 hr, 0.5 µM (Heart-specific genes only)**

```{r SC_8, echo=TRUE, message=FALSE, fig.height=6,fig.width=8}
library(dplyr)
library(ggplot2)
library(org.Hs.eg.db)
library(AnnotationDbi)

# --- Load Heart-Specific Genes ---
heart_genes <- read.csv("data/Human_Heart_Genes.csv", stringsAsFactors = FALSE)
heart_genes$Entrez_ID <- mapIds(
  org.Hs.eg.db,
  keys = heart_genes$Gene,
  column = "ENTREZID",
  keytype = "SYMBOL",
  multiVals = "first"
)
heart_entrez_ids <- na.omit(heart_genes$Entrez_ID) %>% as.character()

# --- Load DEG Data ---
CX_0.5_48 <- read.csv("data/DEGs/Toptable_CX_0.5_48.csv")
DOX_0.5_48 <- read.csv("data/DEGs/Toptable_DOX_0.5_48.csv")

CX_0.5_48$Entrez_ID <- as.character(CX_0.5_48$Entrez_ID)
DOX_0.5_48$Entrez_ID <- as.character(DOX_0.5_48$Entrez_ID)

# --- Merge and filter for heart-specific genes ---
merged_heart_48h_0.5 <- merge(
  CX_0.5_48, DOX_0.5_48,
  by = "Entrez_ID", suffixes = c("_CX", "_DOX")
)

merged_heart_48h_0.5 <- merged_heart_48h_0.5 %>%
  filter(Entrez_ID %in% heart_entrez_ids)

# --- Correlation ---
cor_test <- cor.test(
  merged_heart_48h_0.5$logFC_CX,
  merged_heart_48h_0.5$logFC_DOX,
  method = "pearson"
)

r_val <- round(cor_test$estimate, 3)
p_val <- formatC(cor_test$p.value, format = "e", digits = 2)
label_text <- paste0("r = ", r_val, "\n", "p = ", p_val)

# --- Scatter Plot ---
ggplot(merged_heart_48h_0.5, aes(x = logFC_CX, y = logFC_DOX)) +
  geom_point(alpha = 0.8, color = "black") +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  labs(
    title = "CX vs DOX logFC (48 hr, 0.5 µM, Heart-specific genes only)",
    x = "logFC (CX vs VEH)",
    y = "logFC (DOX vs VEH)"
  ) +
  theme_minimal(base_size = 14) +
  annotate(
    "text",
    x = -Inf, y = Inf,
    hjust = -0.1, vjust = 1.2,
    label = label_text,
    size = 5, fontface = "bold"
  )
```


## **📌 Proportion of DDR DEGs in CX and DOX treated samples**

```{r SC_9, echo=TRUE, message=FALSE, fig.height=8,fig.width=10}
# ------------------ Load Libraries ------------------
library(tidyverse)
library(org.Hs.eg.db)

# ------------------ Define DDR Gene Set ------------------
ddr_entrez <- c(
  10111, 1017, 1019, 1020, 1021, 1026, 1027, 10912, 11011, 1111,
  11200, 1385, 1643, 1647, 1869, 207, 2177, 25, 27113, 27244,
  3014, 317, 355, 4193, 4292, 4361, 4609, 4616, 4683, 472, 50484,
  5366, 5371, 54205, 545, 55367, 5591, 581, 5810, 5883, 5884,
  5888, 5893, 5925, 595, 5981, 6118, 637, 672, 7157, 7799,
  8243, 836, 841, 84126, 842, 8795, 891, 894, 896, 898,
  9133, 9134, 983, 9874, 993, 995, 5916
) %>% as.character()

# ------------------ Load DEG Data ------------------
deg_list <- list(
  "CX_0.1_3"   = read.csv("data/DEGs/Toptable_CX_0.1_3.csv"),
  "CX_0.1_24"  = read.csv("data/DEGs/Toptable_CX_0.1_24.csv"),
  "CX_0.1_48"  = read.csv("data/DEGs/Toptable_CX_0.1_48.csv"),
  "CX_0.5_3"   = read.csv("data/DEGs/Toptable_CX_0.5_3.csv"),
  "CX_0.5_24"  = read.csv("data/DEGs/Toptable_CX_0.5_24.csv"),
  "CX_0.5_48"  = read.csv("data/DEGs/Toptable_CX_0.5_48.csv"),
  "DOX_0.1_3"  = read.csv("data/DEGs/Toptable_DOX_0.1_3.csv"),
  "DOX_0.1_24" = read.csv("data/DEGs/Toptable_DOX_0.1_24.csv"),
  "DOX_0.1_48" = read.csv("data/DEGs/Toptable_DOX_0.1_48.csv"),
  "DOX_0.5_3"  = read.csv("data/DEGs/Toptable_DOX_0.5_3.csv"),
  "DOX_0.5_24" = read.csv("data/DEGs/Toptable_DOX_0.5_24.csv"),
  "DOX_0.5_48" = read.csv("data/DEGs/Toptable_DOX_0.5_48.csv")
)

# ------------------ Compute Proportions ------------------
proportion_data <- map_dfr(names(deg_list), function(sample) {
  sig_df <- deg_list[[sample]] %>% filter(adj.P.Val < 0.05)
  sample_degs <- unique(as.character(sig_df$Entrez_ID))

  yes <- sum(sample_degs %in% ddr_entrez)
  no <- length(sample_degs) - yes

  data.frame(
    Sample = sample,
    Category = c("DDR_DEG", "Non_DDR_DEG"),
    Count = c(yes, no)
  )
}) %>%
  group_by(Sample) %>%
  mutate(Proportion = Count / sum(Count) * 100)

# ------------------ Set Order ------------------
proportion_data$Sample <- factor(proportion_data$Sample, levels = c(
  "CX_0.1_3", "CX_0.1_24", "CX_0.1_48",
  "CX_0.5_3", "CX_0.5_24", "CX_0.5_48",
  "DOX_0.1_3", "DOX_0.1_24", "DOX_0.1_48",
  "DOX_0.5_3", "DOX_0.5_24", "DOX_0.5_48"
))

proportion_data$Category <- factor(proportion_data$Category,
                                   levels = c("DDR_DEG", "Non_DDR_DEG"))

# ------------------ Statistical Testing (CX vs DOX) ------------------
matched_pairs <- list(
  "0.1_3"  = c("CX_0.1_3", "DOX_0.1_3"),
  "0.1_24" = c("CX_0.1_24", "DOX_0.1_24"),
  "0.1_48" = c("CX_0.1_48", "DOX_0.1_48"),
  "0.5_3"  = c("CX_0.5_3", "DOX_0.5_3"),
  "0.5_24" = c("CX_0.5_24", "DOX_0.5_24"),
  "0.5_48" = c("CX_0.5_48", "DOX_0.5_48")
)

test_results <- map_dfr(names(matched_pairs), function(label) {
  cx <- matched_pairs[[label]][1]
  dox <- matched_pairs[[label]][2]

  cx_df <- deg_list[[cx]] %>% filter(adj.P.Val < 0.05)
  dox_df <- deg_list[[dox]] %>% filter(adj.P.Val < 0.05)

  a1 <- sum(cx_df$Entrez_ID %in% ddr_entrez)
  b1 <- nrow(cx_df) - a1
  a2 <- sum(dox_df$Entrez_ID %in% ddr_entrez)
  b2 <- nrow(dox_df) - a2

  mat <- matrix(c(a1, b1, a2, b2), nrow = 2, byrow = TRUE)
  test <- if (min(mat) < 5) fisher.test(mat) else chisq.test(mat)

  data.frame(
    Comparison = label,
    CX_sample = cx,
    DOX_sample = dox,
    a1 = a1, b1 = b1, a2 = a2, b2 = b2,
    P_value = test$p.value,
    Stars = ifelse(test$p.value < 0.05, "*", "")
  )
})

write.csv(test_results, "data/DDR_DEG_overlap_stats.csv", row.names = FALSE)

# ------------------ Plot ------------------
ggplot(proportion_data, aes(x = Sample, y = Proportion, fill = Category)) +
  geom_bar(stat = "identity") +
  geom_text(
    data = test_results %>% filter(Stars != "") %>%
      mutate(Sample = CX_sample, y_pos = 102),
    aes(x = Sample, y = y_pos, label = Stars),
    inherit.aes = FALSE, size = 6
  ) +
  scale_fill_manual(values = c("DDR_DEG" = "#e41a1c", "Non_DDR_DEG" = "#377eb8")) +
  scale_y_continuous(labels = scales::percent_format(scale = 1), limits = c(0, 105)) +
  labs(
    title = "Proportion of DDR genes in CX and DOX DEG Set",
    x = "Sample",
    y = "Percentage of DEGs",
    fill = "Category"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.title = element_blank(),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 1)
  )
```


## **📌 Forest Plot: DDR Gene Enrichment**

```{r SC_10, echo=TRUE, message=FALSE, fig.height=10,fig.width=12}
# --- Libraries ---
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)

# --- Step 1: DDR Gene Set (Entrez IDs) ---
ddr_entrez <- c(
  10111, 1017, 1019, 1020, 1021, 1026, 1027, 10912, 11011, 1111,
  11200, 1385, 1643, 1647, 1869, 207, 2177, 25, 27113, 27244,
  3014, 317, 355, 4193, 4292, 4361, 4609, 4616, 4683, 472, 50484,
  5366, 5371, 54205, 545, 55367, 5591, 581, 5810, 5883, 5884,
  5888, 5893, 5925, 595, 5981, 6118, 637, 672, 7157, 7799,
  8243, 836, 841, 84126, 842, 8795, 891, 894, 896, 898,
  9133, 9134, 983, 9874, 993, 995, 5916
) %>% as.character()

# --- Step 2: Load DEG tables ---
deg_files <- list.files("data/DEGs/", pattern = "Toptable_.*\\.csv", full.names = TRUE)
deg_list  <- lapply(deg_files, read.csv)
names(deg_list) <- gsub("Toptable_|\\.csv", "", basename(deg_files))

# --- Step 3: Fisher test function (save raw counts too) ---
fisher_or <- function(df, sample_name) {
  df <- df %>%
    mutate(
      DEG = adj.P.Val < 0.05,
      DDR_gene = Entrez_ID %in% ddr_entrez
    )

  a <- sum(df$DEG & df$DDR_gene, na.rm = TRUE)   # DDR genes among DEGs
  b <- sum(df$DEG & !df$DDR_gene, na.rm = TRUE)  # Non-DDR among DEGs
  c <- sum(!df$DEG & df$DDR_gene, na.rm = TRUE)  # DDR genes not DEGs
  d <- sum(!df$DEG & !df$DDR_gene, na.rm = TRUE) # Non-DDR not DEGs

  test <- fisher.test(matrix(c(a, b, c, d), nrow = 2))

  tibble(
    Sample = sample_name,
    DE_DDR = a,
    DE_nonDDR = b,
    nonDE_DDR = c,
    nonDE_nonDDR = d,
    OR = unname(test$estimate),
    Lower_CI = test$conf.int[1],
    Upper_CI = test$conf.int[2],
    Pval = test$p.value,
    Stars = case_when(
      test$p.value < 0.001 ~ "***",
      test$p.value < 0.01  ~ "**",
      test$p.value < 0.05  ~ "*",
      TRUE ~ ""
    )
  )
}

# --- Step 4: Run Fisher tests for all DEG files ---
results <- bind_rows(mapply(fisher_or, deg_list, names(deg_list), SIMPLIFY = FALSE))

# --- Step 5: Extract metadata (Drug, Conc, Time) ---
results <- results %>%
  separate(Sample, into = c("Drug","Conc","Time"), sep = "_") %>%
  mutate(
    Label = paste(Drug, Conc, sep = "_"),
    Time = factor(Time, levels = c("3","24","48")) # enforce order
  )

# --- Step 6: Forest Plot ---
ggplot(results, aes(x = Label, y = OR, ymin = Lower_CI, ymax = Upper_CI)) +
  geom_pointrange(color = "black", size = 0.9) +
  geom_text(aes(label = Stars), hjust = -0.5, size = 5) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  coord_flip() +
  facet_wrap(~Time, ncol = 1, scales = "free_y") +
  ylim(0, 20) +   # fixed OR scale
  labs(
    title = "DDR Gene Enrichment Across Conditions",
    x = "Condition (Drug_Conc)",
    y = "Odds Ratio (95% CI)"
  ) +
  theme_classic(base_size = 14) +
  theme(
    legend.position = "none",
    strip.text = element_text(face = "bold", size = 12)
  )

# --- Step 7: Export results (with raw numbers) ---
write.csv(results, "data/DDR_ForestPlot_Data.csv", row.names = FALSE)
```

## **📌 Proportion of Heart-Specific DEGs in CX and DOX treated samples**

```{r SC_11, echo=TRUE, message=FALSE, fig.height=8,fig.width=10}
# ------------------ Load Libraries ------------------
library(tidyverse)
library(org.Hs.eg.db)
library(AnnotationDbi)

# ------------------ Load Heart-Specific Genes ------------------
heart_genes <- read.csv("data/Human_Heart_Genes.csv", stringsAsFactors = FALSE)
heart_genes$Entrez_ID <- mapIds(
  org.Hs.eg.db,
  keys = heart_genes$Gene,
  column = "ENTREZID",
  keytype = "SYMBOL",
  multiVals = "first"
)
heart_entrez_ids <- na.omit(heart_genes$Entrez_ID) %>% as.character()

# ------------------ Load DEG Data ------------------
deg_list <- list(
  "CX_0.1_3"   = read.csv("data/DEGs/Toptable_CX_0.1_3.csv"),
  "CX_0.1_24"  = read.csv("data/DEGs/Toptable_CX_0.1_24.csv"),
  "CX_0.1_48"  = read.csv("data/DEGs/Toptable_CX_0.1_48.csv"),
  "CX_0.5_3"   = read.csv("data/DEGs/Toptable_CX_0.5_3.csv"),
  "CX_0.5_24"  = read.csv("data/DEGs/Toptable_CX_0.5_24.csv"),
  "CX_0.5_48"  = read.csv("data/DEGs/Toptable_CX_0.5_48.csv"),
  "DOX_0.1_3"  = read.csv("data/DEGs/Toptable_DOX_0.1_3.csv"),
  "DOX_0.1_24" = read.csv("data/DEGs/Toptable_DOX_0.1_24.csv"),
  "DOX_0.1_48" = read.csv("data/DEGs/Toptable_DOX_0.1_48.csv"),
  "DOX_0.5_3"  = read.csv("data/DEGs/Toptable_DOX_0.5_3.csv"),
  "DOX_0.5_24" = read.csv("data/DEGs/Toptable_DOX_0.5_24.csv"),
  "DOX_0.5_48" = read.csv("data/DEGs/Toptable_DOX_0.5_48.csv")
)

# ------------------ Compute Proportions ------------------
proportion_data <- map_dfr(names(deg_list), function(sample) {
  sig_df <- deg_list[[sample]] %>% filter(adj.P.Val < 0.05)
  sample_degs <- unique(as.character(sig_df$Entrez_ID))

  yes <- sum(sample_degs %in% heart_entrez_ids)
  no <- length(sample_degs) - yes

  data.frame(
    Sample = sample,
    Category = c("Heart_DEG", "Non_Heart_DEG"),
    Count = c(yes, no)
  )
}) %>%
  group_by(Sample) %>%
  mutate(Proportion = Count / sum(Count) * 100)

# ------------------ Set Order ------------------
proportion_data$Sample <- factor(proportion_data$Sample, levels = c(
  "CX_0.1_3", "CX_0.1_24", "CX_0.1_48",
  "CX_0.5_3", "CX_0.5_24", "CX_0.5_48",
  "DOX_0.1_3", "DOX_0.1_24", "DOX_0.1_48",
  "DOX_0.5_3", "DOX_0.5_24", "DOX_0.5_48"
))

proportion_data$Category <- factor(proportion_data$Category,
                                   levels = c("Heart_DEG", "Non_Heart_DEG"))

# ------------------ Statistical Testing (CX vs DOX) ------------------
matched_pairs <- list(
  "0.1_3"  = c("CX_0.1_3", "DOX_0.1_3"),
  "0.1_24" = c("CX_0.1_24", "DOX_0.1_24"),
  "0.1_48" = c("CX_0.1_48", "DOX_0.1_48"),
  "0.5_3"  = c("CX_0.5_3", "DOX_0.5_3"),
  "0.5_24" = c("CX_0.5_24", "DOX_0.5_24"),
  "0.5_48" = c("CX_0.5_48", "DOX_0.5_48")
)

test_results <- map_dfr(names(matched_pairs), function(label) {
  cx <- matched_pairs[[label]][1]
  dox <- matched_pairs[[label]][2]

  cx_df <- deg_list[[cx]] %>% filter(adj.P.Val < 0.05)
  dox_df <- deg_list[[dox]] %>% filter(adj.P.Val < 0.05)

  a1 <- sum(cx_df$Entrez_ID %in% heart_entrez_ids)
  b1 <- nrow(cx_df) - a1
  a2 <- sum(dox_df$Entrez_ID %in% heart_entrez_ids)
  b2 <- nrow(dox_df) - a2

  mat <- matrix(c(a1, b1, a2, b2), nrow = 2, byrow = TRUE)
  test <- if (min(mat) < 5) fisher.test(mat) else chisq.test(mat)

  data.frame(
    Comparison = label,
    CX_sample = cx,
    DOX_sample = dox,
    P_value = test$p.value,
    Stars = ifelse(test$p.value < 0.05, "*", "")
  )
})

write.csv(test_results, "data/Heart_DEG_overlap_stats.csv", row.names = FALSE)

# ------------------ Plot ------------------
ggplot(proportion_data, aes(x = Sample, y = Proportion, fill = Category)) +
  geom_bar(stat = "identity") +
  geom_text(
    data = test_results %>% filter(Stars != "") %>%
      mutate(Sample = CX_sample, y_pos = 102),
    aes(x = Sample, y = y_pos, label = Stars),
    inherit.aes = FALSE, size = 6
  ) +
  scale_fill_manual(values = c("Heart_DEG" = "#e41a1c", "Non_Heart_DEG" = "#377eb8")) +
  scale_y_continuous(labels = scales::percent_format(scale = 1), limits = c(0, 105)) +
  labs(
    title = "Proportion of Heart-Specific DEGs in CX and DOX treated samples",
    x = "Sample",
    y = "Percentage of DEGs",
    fill = "Category"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.title = element_blank(),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 1)
  )
```

## **📌 Forest Plot: Heart-Specific Gene Enrichment**

```{r SC_12, echo=TRUE, message=FALSE, fig.height=10,fig.width=12}
# --- Libraries ---
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
library(org.Hs.eg.db)
library(AnnotationDbi)

# --- Step 1: Load Heart-Specific Genes ---
heart_genes <- read.csv("data/Human_Heart_Genes.csv", stringsAsFactors = FALSE)
heart_genes$Entrez_ID <- mapIds(
  org.Hs.eg.db,
  keys = heart_genes$Gene,
  column = "ENTREZID",
  keytype = "SYMBOL",
  multiVals = "first"
)
heart_entrez_ids <- na.omit(heart_genes$Entrez_ID) %>% as.character()

# --- Step 2: Load DEG tables ---
deg_files <- list.files("data/DEGs/", pattern = "Toptable_.*\\.csv", full.names = TRUE)
deg_list  <- lapply(deg_files, read.csv)
names(deg_list) <- gsub("Toptable_|\\.csv", "", basename(deg_files))

# --- Step 3: Fisher test function ---
fisher_or <- function(df, sample_name) {
  df <- df %>%
    mutate(
      DEG = adj.P.Val < 0.05,
      HeartGene = Entrez_ID %in% heart_entrez_ids
    )

  a <- sum(df$DEG & df$HeartGene, na.rm = TRUE)
  b <- sum(df$DEG & !df$HeartGene, na.rm = TRUE)
  c <- sum(!df$DEG & df$HeartGene, na.rm = TRUE)
  d <- sum(!df$DEG & !df$HeartGene, na.rm = TRUE)

  test <- fisher.test(matrix(c(a, b, c, d), nrow = 2))

  tibble(
    Sample = sample_name,
    DE_Heart = a,
    DE_nonHeart = b,
    nonDE_Heart = c,
    nonDE_nonHeart = d,
    OR = unname(test$estimate),
    Lower_CI = test$conf.int[1],
    Upper_CI = test$conf.int[2],
    Pval = test$p.value,
    Stars = case_when(
      test$p.value < 0.001 ~ "***",
      test$p.value < 0.01  ~ "**",
      test$p.value < 0.05  ~ "*",
      TRUE ~ ""
    )
  )
}

# --- Step 4: Run Fisher tests ---
results <- bind_rows(mapply(fisher_or, deg_list, names(deg_list), SIMPLIFY = FALSE))

# --- Step 5: Extract metadata ---
results <- results %>%
  separate(Sample, into = c("Drug","Conc","Time"), sep = "_") %>%
  mutate(
    Label = paste(Drug, Conc, sep = "_"),
    Time = factor(Time, levels = c("3","24","48"))
  )

# --- Step 6: Forest plot ---
ggplot(results, aes(x = Label, y = OR, ymin = Lower_CI, ymax = Upper_CI)) +
  geom_pointrange(aes(color = Pval < 0.05), size = 0.9) +
  geom_text(aes(label = Stars), hjust = -0.5, size = 5) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "grey40")) +
  coord_flip() +
  facet_wrap(~Time, ncol = 1, scales = "free_y") +
  ylim(0, 20) +
  labs(
    title = "Heart-Specific Gene Enrichment Across Conditions",
    x = "Condition (Drug_Conc)",
    y = "Odds Ratio (95% CI)"
  ) +
  theme_classic(base_size = 14) +
  theme(
    legend.position = "none",
    strip.text = element_text(face = "bold", size = 12)
  )

# --- Step 7: Export results with raw counts ---
write.csv(results, "data/HeartSpecific_ForestPlot_Data.csv", row.names = FALSE)
```


## **📌 Proportion of DDR Genes (CorrMotif Groups)**

```{r SC_13, echo=TRUE, message=FALSE, fig.height=10,fig.width=12}
# ----------------- Load Required Libraries -----------------
library(dplyr)
library(ggplot2)

# ----------------- Load DDR Genes -----------------
ddr_entrez <- c(
  10111, 1017, 1019, 1020, 1021, 1026, 1027, 10912, 11011, 1111,
  11200, 1385, 1643, 1647, 1869, 207, 2177, 25, 27113, 27244,
  3014, 317, 355, 4193, 4292, 4361, 4609, 4616, 4683, 472, 50484,
  5366, 5371, 54205, 545, 55367, 5591, 581, 5810, 5883, 5884,
  5888, 5893, 5925, 595, 5981, 6118, 637, 672, 7157, 7799,
  8243, 836, 841, 84126, 842, 8795, 891, 894, 896, 898,
  9133, 9134, 983, 9874, 993, 995, 5916
) %>% as.character()

# ----------------- Load CorrMotif Groups -----------------
# 0.1 µM
prob_1_0.1 <- as.character(read.csv("data/prob_1_0.1.csv")$Entrez_ID)
prob_2_0.1 <- as.character(read.csv("data/prob_2_0.1.csv")$Entrez_ID)
prob_3_0.1 <- as.character(read.csv("data/prob_3_0.1.csv")$Entrez_ID)

# 0.5 µM
prob_1_0.5 <- as.character(read.csv("data/prob_1_0.5.csv")$Entrez_ID)
prob_2_0.5 <- as.character(read.csv("data/prob_2_0.5.csv")$Entrez_ID)
prob_3_0.5 <- as.character(read.csv("data/prob_3_0.5.csv")$Entrez_ID)
prob_4_0.5 <- as.character(read.csv("data/prob_4_0.5.csv")$Entrez_ID)
prob_5_0.5 <- as.character(read.csv("data/prob_5_0.5.csv")$Entrez_ID)

# ----------------- Annotate CorrMotif Groups -----------------
df_0.1 <- data.frame(Entrez_ID = unique(c(prob_1_0.1, prob_2_0.1, prob_3_0.1))) %>%
  mutate(
    Response_Group = case_when(
      Entrez_ID %in% prob_1_0.1 ~ "Non response (0.1)",
      Entrez_ID %in% prob_2_0.1 ~ "CX_DOX_1",
      Entrez_ID %in% prob_3_0.1 ~ "DOX_sp_1"
    ),
    Category = ifelse(Entrez_ID %in% ddr_entrez, "DDR Genes", "Non-DDR Genes"),
    Concentration = "0.1"
  )

df_0.5 <- data.frame(Entrez_ID = unique(c(prob_1_0.5, prob_2_0.5, prob_3_0.5, prob_4_0.5, prob_5_0.5))) %>%
  mutate(
    Response_Group = case_when(
      Entrez_ID %in% prob_1_0.5 ~ "Non response (0.5)",
      Entrez_ID %in% prob_2_0.5 ~ "DOX_sp_2",
      Entrez_ID %in% prob_3_0.5 ~ "DOX_sp_3",
      Entrez_ID %in% prob_4_0.5 ~ "CX_DOX_2",
      Entrez_ID %in% prob_5_0.5 ~ "CX_DOX_3"
    ),
    Category = ifelse(Entrez_ID %in% ddr_entrez, "DDR Genes", "Non-DDR Genes"),
    Concentration = "0.5"
  )

# ----------------- Combine Data -----------------
df_combined <- bind_rows(df_0.1, df_0.5)

# ----------------- Calculate Proportions -----------------
proportion_data <- df_combined %>%
  group_by(Concentration, Response_Group, Category) %>%
  summarise(Count = n(), .groups = "drop") %>%
  group_by(Concentration, Response_Group) %>%
  mutate(Percentage = Count / sum(Count) * 100)

# ----------------- Fisher's Exact Test -----------------
run_fisher_test <- function(df, ref_group) {
  ref_counts <- df %>%
    filter(Response_Group == ref_group) %>%
    dplyr::select(Category, Count) %>%
    {setNames(.$Count, .$Category)}

  df %>%
    filter(Response_Group != ref_group) %>%
    group_by(Response_Group) %>%
    summarise(
      p_value = {
        group_counts <- Count[Category %in% c("DDR Genes", "Non-DDR Genes")]
        if (length(group_counts) < 2) group_counts <- c(group_counts, 0)
        contingency_table <- matrix(c(
          group_counts[1], group_counts[2],
          ref_counts["DDR Genes"], ref_counts["Non-DDR Genes"]
        ), nrow = 2)
        fisher.test(contingency_table)$p.value
      },
      .groups = "drop"
    ) %>%
    mutate(Significance = ifelse(!is.na(p_value) & p_value < 0.05, "*", ""))
}

# Run Fisher’s test for each concentration
fisher_0.1 <- run_fisher_test(proportion_data %>% filter(Concentration == "0.1"), "Non response (0.1)")
fisher_0.5 <- run_fisher_test(proportion_data %>% filter(Concentration == "0.5"), "Non response (0.5)")

fisher_all <- bind_rows(
  fisher_0.1 %>% mutate(Concentration = "0.1"),
  fisher_0.5 %>% mutate(Concentration = "0.5")
)

# ----------------- Merge Fisher Results -----------------
proportion_data <- proportion_data %>%
  left_join(fisher_all, by = c("Concentration", "Response_Group"))

# ----------------- Reorder Groups -----------------
proportion_data$Response_Group <- factor(proportion_data$Response_Group, levels = c(
  "Non response (0.1)", "CX_DOX_1", "DOX_sp_1",
  "Non response (0.5)", "DOX_sp_2", "DOX_sp_3", "CX_DOX_2", "CX_DOX_3"
))

# ----------------- Star Labels -----------------
label_data <- proportion_data %>%
  group_by(Concentration, Response_Group) %>%
  summarise(Significance = dplyr::first(Significance), .groups = "drop") %>%
  filter(!is.na(Significance)) %>%
  mutate(y_pos = 100)

# ----------------- Plot -----------------
ggplot(proportion_data, aes(x = Response_Group, y = Percentage, fill = Category)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(
    data = label_data,
    aes(x = Response_Group, y = y_pos, label = Significance),
    inherit.aes = FALSE,
    size = 5,
    color = "black"
  ) +
  facet_wrap(~ Concentration, scales = "free_x") +
  scale_fill_manual(values = c("DDR Genes" = "#e41a1c", "Non-DDR Genes" = "#377eb8")) +
  scale_y_continuous(limits = c(0, 110), expand = c(0, 0)) +
  labs(
    title = "DDR Gene Proportions Across CorrMotif Groups",
    x = "Response Groups",
    y = "Percentage of Genes",
    fill = "Gene Category"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5, face = "bold"),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text.x = element_text(size = 11, angle = 45, hjust = 1),
    axis.text.y = element_text(size = 12),
    legend.title = element_text(size = 13),
    legend.text = element_text(size = 12),
    strip.text = element_text(size = 14, face = "bold"),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 1.2),
    panel.spacing = unit(1.2, "lines")
  )
```

## **📌 Odds Ratios for CorrMotif Groups (DDR genes)**

```{r SC_14, echo=TRUE, message=FALSE, fig.height=10,fig.width=12}
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)

# --- Load DDR Gene Entrez IDs ---
ddr_entrez <- c(
  10111, 1017, 1019, 1020, 1021, 1026, 1027, 10912, 11011, 1111,
  11200, 1385, 1643, 1647, 1869, 207, 2177, 25, 27113, 27244,
  3014, 317, 355, 4193, 4292, 4361, 4609, 4616, 4683, 472, 50484,
  5366, 5371, 54205, 545, 55367, 5591, 581, 5810, 5883, 5884,
  5888, 5893, 5925, 595, 5981, 6118, 637, 672, 7157, 7799,
  8243, 836, 841, 84126, 842, 8795, 891, 894, 896, 898,
  9133, 9134, 983, 9874, 993, 995, 5916
) %>% as.character()

# --- Load CorrMotif Groups ---
# 0.1 µM
prob_1_0.1 <- as.character(read.csv("data/prob_1_0.1.csv")$Entrez_ID)
prob_2_0.1 <- as.character(read.csv("data/prob_2_0.1.csv")$Entrez_ID)
prob_3_0.1 <- as.character(read.csv("data/prob_3_0.1.csv")$Entrez_ID)

# 0.5 µM
prob_1_0.5 <- as.character(read.csv("data/prob_1_0.5.csv")$Entrez_ID)
prob_2_0.5 <- as.character(read.csv("data/prob_2_0.5.csv")$Entrez_ID)
prob_3_0.5 <- as.character(read.csv("data/prob_3_0.5.csv")$Entrez_ID)
prob_4_0.5 <- as.character(read.csv("data/prob_4_0.5.csv")$Entrez_ID)
prob_5_0.5 <- as.character(read.csv("data/prob_5_0.5.csv")$Entrez_ID)

# --- Annotate Groups ---
df_0.1 <- data.frame(Entrez_ID = unique(c(prob_1_0.1, prob_2_0.1, prob_3_0.1))) %>%
  mutate(
    Response_Group = case_when(
      Entrez_ID %in% prob_1_0.1 ~ "Non response (0.1)",
      Entrez_ID %in% prob_2_0.1 ~ "CX_DOX_1",
      Entrez_ID %in% prob_3_0.1 ~ "DOX_sp_1"
    ),
    Category = ifelse(Entrez_ID %in% ddr_entrez, "DDR Genes", "Non-DDR Genes"),
    Concentration = "0.1"
  )

df_0.5 <- data.frame(Entrez_ID = unique(c(prob_1_0.5, prob_2_0.5, prob_3_0.5, prob_4_0.5, prob_5_0.5))) %>%
  mutate(
    Response_Group = case_when(
      Entrez_ID %in% prob_1_0.5 ~ "Non response (0.5)",
      Entrez_ID %in% prob_2_0.5 ~ "DOX_sp_2",
      Entrez_ID %in% prob_3_0.5 ~ "DOX_sp_3",
      Entrez_ID %in% prob_4_0.5 ~ "CX_DOX_2",
      Entrez_ID %in% prob_5_0.5 ~ "CX_DOX_3"
    ),
    Category = ifelse(Entrez_ID %in% ddr_entrez, "DDR Genes", "Non-DDR Genes"),
    Concentration = "0.5"
  )

df_combined <- bind_rows(df_0.1, df_0.5)

# --- Fisher Odds Ratio Function ---
fisher_or_group <- function(df_group, df_all, group_name, conc) {
  # counts in group
  a <- sum(df_group$Category == "DDR Genes")
  b <- sum(df_group$Category == "Non-DDR Genes")

  # counts in rest of groups at same conc
  ref <- df_all %>% filter(Response_Group != group_name)
  c <- sum(ref$Category == "DDR Genes")
  d <- sum(ref$Category == "Non-DDR Genes")

  mat <- matrix(c(a, b, c, d), nrow = 2)
  if (any(mat == 0)) mat <- mat + 0.5  # continuity correction

  test <- fisher.test(mat)

  tibble(
    Response_Group = group_name,
    Concentration  = conc,
    a = a, b = b, c = c, d = d,
    OR = unname(test$estimate),
    Lower_CI = test$conf.int[1],
    Upper_CI = test$conf.int[2],
    Pval = test$p.value,
    Stars = case_when(
      test$p.value < 0.001 ~ "***",
      test$p.value < 0.01  ~ "**",
      test$p.value < 0.05  ~ "*",
      TRUE ~ ""
    )
  )
}

# --- Run Fisher tests ---
results <- list()
for (conc in unique(df_combined$Concentration)) {
  conc_df <- df_combined %>% filter(Concentration == conc)
  for (grp in unique(conc_df$Response_Group)) {
    grp_df <- conc_df %>% filter(Response_Group == grp)
    results[[paste(conc, grp)]] <- fisher_or_group(grp_df, conc_df, grp, conc)
  }
}
results <- bind_rows(results)

# --- Save Results ---
write.csv(results, "data/CorrMotif_DDRGenes_OddsRatios.csv", row.names = FALSE)

# --- Forest Plot ---
ggplot(results, aes(x = Response_Group, y = OR, ymin = Lower_CI, ymax = Upper_CI)) +
  geom_pointrange(aes(color = Pval < 0.05), size = 0.9) +
  geom_text(aes(label = Stars), hjust = -0.5, size = 5) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "grey40")) +
  coord_flip() +
  facet_wrap(~Concentration, ncol = 1, scales = "free_y") +
  ylim(0, 20) +
  labs(
    title = "DDR Gene Enrichment Across CorrMotif Groups",
    x = "Response Group",
    y = "Odds Ratio (95% CI)"
  ) +
  theme_classic(base_size = 14) +
  theme(
    legend.position = "none",
    strip.text = element_text(face = "bold", size = 12)
  )
```

## **📌 Violin-Boxplot: TS Score in 12 DEG samples**

```{r SC_15, echo=TRUE, message=FALSE, fig.height=10,fig.width=12}
# 📦 Load Required Libraries
library(ggplot2)
library(dplyr)
library(tidyr)

# ✅ Step 1: Load DEG files
deg_list <- list(
  "CX_0.1_3"   = read.csv("data/DEGs/Toptable_CX_0.1_3.csv"),
  "CX_0.1_24"  = read.csv("data/DEGs/Toptable_CX_0.1_24.csv"),
  "CX_0.1_48"  = read.csv("data/DEGs/Toptable_CX_0.1_48.csv"),
  "CX_0.5_3"   = read.csv("data/DEGs/Toptable_CX_0.5_3.csv"),
  "CX_0.5_24"  = read.csv("data/DEGs/Toptable_CX_0.5_24.csv"),
  "CX_0.5_48"  = read.csv("data/DEGs/Toptable_CX_0.5_48.csv"),
  "DOX_0.1_3"  = read.csv("data/DEGs/Toptable_DOX_0.1_3.csv"),
  "DOX_0.1_24" = read.csv("data/DEGs/Toptable_DOX_0.1_24.csv"),
  "DOX_0.1_48" = read.csv("data/DEGs/Toptable_DOX_0.1_48.csv"),
  "DOX_0.5_3"  = read.csv("data/DEGs/Toptable_DOX_0.5_3.csv"),
  "DOX_0.5_24" = read.csv("data/DEGs/Toptable_DOX_0.5_24.csv"),
  "DOX_0.5_48" = read.csv("data/DEGs/Toptable_DOX_0.5_48.csv")
)

# ✅ Step 2: Load TS data
ts_data <- read.csv("data/TS.csv") %>%
  mutate(Entrez_ID = as.character(Entrez_ID))

# ✅ Step 3: Merge DEGs with TS scores
ts_long <- bind_rows(lapply(names(deg_list), function(name) {
  df <- deg_list[[name]] %>% filter(adj.P.Val < 0.05)
  df$Sample <- name
  df
})) %>%
  mutate(Entrez_ID = as.character(Entrez_ID)) %>%
  left_join(ts_data, by = "Entrez_ID") %>%
  separate(Sample, into = c("Drug","Conc","Time"), sep = "_") %>%
  mutate(
    Heart_Ventricle = as.numeric(Heart_Ventricle),
    Conc = factor(Conc, levels = c("0.1","0.5")),
    Time = factor(Time, levels = c("3","24","48"))   # ✅ enforce order
  ) %>%
  filter(!is.na(Heart_Ventricle))

# ✅ Step 4: Define CX vs DOX comparison table
comparison_table <- expand.grid(
  Conc = c("0.1","0.5"),
  Time = c("3","24","48"),
  stringsAsFactors = FALSE
)

# ✅ Step 5: Run Wilcoxon tests
star_df <- lapply(1:nrow(comparison_table), function(i) {
  conc <- comparison_table$Conc[i]
  time <- comparison_table$Time[i]

  cx_vals <- ts_long$Heart_Ventricle[ts_long$Drug == "CX" & ts_long$Conc == conc & ts_long$Time == time]
  dox_vals <- ts_long$Heart_Ventricle[ts_long$Drug == "DOX" & ts_long$Conc == conc & ts_long$Time == time]

  cx_vals <- cx_vals[!is.na(cx_vals)]
  dox_vals <- dox_vals[!is.na(dox_vals)]

  if (length(cx_vals) > 2 & length(dox_vals) > 2) {
    test_result <- wilcox.test(cx_vals, dox_vals)
    pval <- test_result$p.value

    if (pval < 0.05) {
      label <- case_when(
        pval < 0.001 ~ "***",
        pval < 0.01  ~ "**",
        TRUE ~ "*"
      )
      y_pos <- max(c(cx_vals, dox_vals), na.rm = TRUE) + 0.4
      return(data.frame(
        Conc = conc, Time = factor(time, levels = c("3","24","48")), # ✅ enforce order here too
        label = label,
        y_pos = y_pos
      ))
    }
  }
  return(NULL)
}) %>% bind_rows()

# ✅ Step 6: Define colors
drug_colors <- c("CX" = "#1f78b4", "DOX" = "#e31a1c")

# ✅ Step 7: Violin + Boxplot
p <- ggplot(ts_long, aes(x = Drug, y = Heart_Ventricle, fill = Drug)) +
  geom_violin(trim = FALSE, scale = "width", color = "black", alpha = 0.8) +
  geom_boxplot(width = 0.2, color = "black", fill = "white", outlier.shape = NA) +
  facet_grid(Conc ~ Time, scales = "free_x") +
  scale_fill_manual(values = drug_colors) +
  scale_y_continuous(
    limits = c(-10, max(ts_long$Heart_Ventricle, na.rm = TRUE) + 2),
    breaks = seq(-10, 25, 5)
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  geom_text(
    data = star_df,
    aes(x = 1.5, y = y_pos, label = label),
    inherit.aes = FALSE,
    size = 6,
    fontface = "bold"
  ) +
  labs(
    title = "Violin-Boxplot: Heart Ventricle TS (CX vs DOX DEGs)",
    y = "Tissue specificity score (Heart Ventricle)",
    x = ""
  ) +
  theme_bw() +
  theme(
    axis.text.x = element_text(size = 12),
    strip.text = element_text(size = 12, face = "bold"),
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    legend.position = "none"
  )

print(p)
```


## **📌 DOX-Cardiotoxicity Gene Set Scatter Plot: CX vs DOX (0.5 µM, 24 hr)**

```{r SC_16, echo=TRUE, message=FALSE, fig.height=6,fig.width=8}
library(ggplot2)

# --- Load Data ---
CX_0.5_24 <- read.csv("data/DEGs/Toptable_CX_0.5_24.csv")
DOX_0.5_24 <- read.csv("data/DEGs/Toptable_DOX_0.5_24.csv")

# --- Ensure Entrez_ID is character ---
CX_0.5_24$Entrez_ID <- as.character(CX_0.5_24$Entrez_ID)
DOX_0.5_24$Entrez_ID <- as.character(DOX_0.5_24$Entrez_ID)

# --- Merge on Entrez_ID ---
merged_24h_0.5 <- merge(
  CX_0.5_24, DOX_0.5_24,
  by = "Entrez_ID", suffixes = c("_CX", "_DOX")
)

# --- DOX-Cardiotoxicity Signature Entrez IDs ---
Entrez_IDs <- c(
  847, 873, 2064, 2878, 2944, 3038, 4846, 51196, 5880, 6687,
  7799, 4292, 5916, 3077, 51310, 9154, 64078, 5244, 10057, 10060,
  89845, 56853, 4625, 1573, 79890
)

# --- Subset merged data ---
cardio_set <- merged_24h_0.5[merged_24h_0.5$Entrez_ID %in% Entrez_IDs, ]

# --- Correlation ---
cor_test <- cor.test(
  cardio_set$logFC_CX,
  cardio_set$logFC_DOX,
  method = "pearson"
)

r_val <- round(cor_test$estimate, 3)
p_val <- formatC(cor_test$p.value, format = "e", digits = 2)
label_text <- paste0("r = ", r_val, "\n", "p = ", p_val)

# --- Scatter Plot (same style as 48 hr plot) ---
ggplot(cardio_set, aes(x = logFC_CX, y = logFC_DOX)) +
  geom_point(alpha = 0.5, color = "black") +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  labs(
    title = "CX vs DOX logFC (24 hr, 0.5 µM)",
    subtitle = "DOX-Cardiotoxicity Gene Set",
    x = "logFC (CX vs VEH)",
    y = "logFC (DOX vs VEH)"
  ) +
  theme_minimal(base_size = 14) +
  annotate(
    "text",
    x = -Inf, y = Inf, hjust = -0.1, vjust = 1.2,
    label = label_text,
    size = 5, fontface = "bold"
  )
```

## **📌 DOX-Cardiotoxicity Gene Set Scatter Plot: CX vs DOX (0.5 µM, 48 hr)**

```{r SC_17, echo=TRUE, message=FALSE, fig.height=6,fig.width=8}
library(ggplot2)

# --- Load Data ---
CX_0.5_48 <- read.csv("data/DEGs/Toptable_CX_0.5_48.csv")
DOX_0.5_48 <- read.csv("data/DEGs/Toptable_DOX_0.5_48.csv")

# --- Ensure Entrez_ID is character ---
CX_0.5_48$Entrez_ID <- as.character(CX_0.5_48$Entrez_ID)
DOX_0.5_48$Entrez_ID <- as.character(DOX_0.5_48$Entrez_ID)

# --- Merge on Entrez_ID ---
merged_48h_0.5 <- merge(
  CX_0.5_48, DOX_0.5_48,
  by = "Entrez_ID", suffixes = c("_CX", "_DOX")
)

# --- DOX-Cardiotoxicity Signature Entrez IDs ---
Entrez_IDs <- c(
  847, 873, 2064, 2878, 2944, 3038, 4846, 51196, 5880, 6687,
  7799, 4292, 5916, 3077, 51310, 9154, 64078, 5244, 10057, 10060,
  89845, 56853, 4625, 1573, 79890
)

# --- Subset merged data ---
cardio_set_48 <- merged_48h_0.5[merged_48h_0.5$Entrez_ID %in% Entrez_IDs, ]

# --- Correlation ---
cor_test <- cor.test(
  cardio_set_48$logFC_CX,
  cardio_set_48$logFC_DOX,
  method = "pearson"
)

r_val <- round(cor_test$estimate, 3)
p_val <- formatC(cor_test$p.value, format = "e", digits = 2)
label_text <- paste0("r = ", r_val, "\n", "p = ", p_val)

# --- Scatter Plot (same publication style) ---
ggplot(cardio_set_48, aes(x = logFC_CX, y = logFC_DOX)) +
  geom_point(alpha = 0.5, color = "black") +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  labs(
    title = "CX vs DOX logFC (48 hr, 0.5 µM)",
    subtitle = "DOX-Cardiotoxicity Gene Set",
    x = "logFC (CX vs VEH)",
    y = "logFC (DOX vs VEH)"
  ) +
  theme_minimal(base_size = 14) +
  annotate(
    "text",
    x = -Inf, y = Inf, hjust = -0.1, vjust = 1.2,
    label = label_text,
    size = 5, fontface = "bold"
  )
```

## **📌 Heart Failure Gene Set Scatter Plot: CX vs DOX (0.5 µM, 24 hr)**

```{r SC_18, echo=TRUE, message=FALSE, fig.height=6,fig.width=8}
library(ggplot2)
library(dplyr)

# --- Load Data ---
CX_0.5_24 <- read.csv("data/DEGs/Toptable_CX_0.5_24.csv")
DOX_0.5_24 <- read.csv("data/DEGs/Toptable_DOX_0.5_24.csv")

# --- Ensure Entrez_ID is character ---
CX_0.5_24$Entrez_ID <- as.character(CX_0.5_24$Entrez_ID)
DOX_0.5_24$Entrez_ID <- as.character(DOX_0.5_24$Entrez_ID)

# --- Merge on Entrez_ID ---
merged_24h_0.5 <- merge(
  CX_0.5_24, DOX_0.5_24,
  by = "Entrez_ID", suffixes = c("_CX", "_DOX")
)

# --- Heart Failure Gene Set ---
entrez_ids <- c(
  9709, 8882, 4023, 29959, 5496, 3992, 9415, 5308, 1026, 54437, 79068, 10221,
  9031, 1187, 1952, 3705, 84722, 7273, 23293, 155382, 9531, 602, 27258, 84163,
  81846, 79933, 56911, 64753, 93210, 1021, 283450, 5998, 57602, 114991, 7073,
  3156, 100101267, 22996, 285025, 11080, 11124, 54810, 7531, 27241, 4774, 57794,
  463, 91319, 6598, 9640, 2186, 26010, 80816, 571, 88, 51652, 64788, 90523, 2969,
  7781, 80777, 10725, 23387, 817, 134728, 8842, 949, 6934, 129787, 10327, 202052,
  2318, 5578, 6801, 6311, 10019, 80724, 217, 84909, 388591, 55101, 9839, 27161,
  5310, 387119, 4641, 5587, 55188, 222553, 9960, 22852, 10087, 9570, 54497,
  200942, 26249, 4137, 375056, 5409, 64116, 8291, 22876, 339855, 4864, 5142,
  221692, 55023, 51426, 6146, 84251, 8189, 27332, 57099, 1869, 1112, 23327,
  11264, 6001
) %>% as.character()

# --- Subset merged data ---
heart_set <- merged_24h_0.5[merged_24h_0.5$Entrez_ID %in% entrez_ids, ]

# --- Correlation ---
cor_test <- cor.test(
  heart_set$logFC_CX,
  heart_set$logFC_DOX,
  method = "pearson"
)

r_val <- round(cor_test$estimate, 3)
p_val <- formatC(cor_test$p.value, format = "e", digits = 2)
label_text <- paste0("r = ", r_val, "\n", "p = ", p_val)

# --- Scatter Plot (same style) ---
ggplot(heart_set, aes(x = logFC_CX, y = logFC_DOX)) +
  geom_point(alpha = 0.5, color = "black") +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  labs(
    title = "CX vs DOX logFC (24 hr, 0.5 µM)",
    subtitle = "Heart Failure Gene Set",
    x = "logFC (CX vs VEH)",
    y = "logFC (DOX vs VEH)"
  ) +
  theme_minimal(base_size = 14) +
  annotate(
    "text",
    x = -Inf, y = Inf,
    hjust = -0.1, vjust = 1.2,
    label = label_text,
    size = 5, fontface = "bold"
  )
```

## **📌 Heart Failure Gene Set Scatter Plot: CX vs DOX (0.5 µM, 48 hr)**

```{r SC_19, echo=TRUE, message=FALSE, fig.height=6,fig.width=8}
library(ggplot2)
library(dplyr)

# --- Load Data ---
CX_0.5_48 <- read.csv("data/DEGs/Toptable_CX_0.5_48.csv")
DOX_0.5_48 <- read.csv("data/DEGs/Toptable_DOX_0.5_48.csv")

# --- Ensure Entrez_ID is character ---
CX_0.5_48$Entrez_ID <- as.character(CX_0.5_48$Entrez_ID)
DOX_0.5_48$Entrez_ID <- as.character(DOX_0.5_48$Entrez_ID)

# --- Merge on Entrez_ID ---
merged_48h_0.5 <- merge(
  CX_0.5_48, DOX_0.5_48,
  by = "Entrez_ID", suffixes = c("_CX", "_DOX")
)

# --- Heart Failure Gene Set ---
entrez_ids <- c(
  9709, 8882, 4023, 29959, 5496, 3992, 9415, 5308, 1026, 54437, 79068, 10221,
  9031, 1187, 1952, 3705, 84722, 7273, 23293, 155382, 9531, 602, 27258, 84163,
  81846, 79933, 56911, 64753, 93210, 1021, 283450, 5998, 57602, 114991, 7073,
  3156, 100101267, 22996, 285025, 11080, 11124, 54810, 7531, 27241, 4774, 57794,
  463, 91319, 6598, 9640, 2186, 26010, 80816, 571, 88, 51652, 64788, 90523, 2969,
  7781, 80777, 10725, 23387, 817, 134728, 8842, 949, 6934, 129787, 10327, 202052,
  2318, 5578, 6801, 6311, 10019, 80724, 217, 84909, 388591, 55101, 9839, 27161,
  5310, 387119, 4641, 5587, 55188, 222553, 9960, 22852, 10087, 9570, 54497,
  200942, 26249, 4137, 375056, 5409, 64116, 8291, 22876, 339855, 4864, 5142,
  221692, 55023, 51426, 6146, 84251, 8189, 27332, 57099, 1869, 1112, 23327,
  11264, 6001
) %>% as.character()

# --- Subset merged data ---
heart_set_48 <- merged_48h_0.5[merged_48h_0.5$Entrez_ID %in% entrez_ids, ]

# --- Correlation ---
cor_test <- cor.test(
  heart_set_48$logFC_CX,
  heart_set_48$logFC_DOX,
  method = "pearson"
)

r_val <- round(cor_test$estimate, 3)
p_val <- formatC(cor_test$p.value, format = "e", digits = 2)
label_text <- paste0("r = ", r_val, "\n", "p = ", p_val)

# --- Scatter Plot (matching style) ---
ggplot(heart_set_48, aes(x = logFC_CX, y = logFC_DOX)) +
  geom_point(alpha = 0.5, color = "black") +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  labs(
    title = "CX vs DOX logFC (48 hr, 0.5 µM)",
    subtitle = "Heart Failure Gene Set",
    x = "logFC (CX vs VEH)",
    y = "logFC (DOX vs VEH)"
  ) +
  theme_minimal(base_size = 14) +
  annotate(
    "text",
    x = -Inf, y = Inf,
    hjust = -0.1, vjust = 1.2,
    label = label_text,
    size = 5, fontface = "bold"
  )
```

## **📌 Forest Plot: Atrial Fibrillation (AF) Risk Loci Enrichment**

```{r SC_20, echo=TRUE, message=FALSE, fig.height=10,fig.width=12}
# --- Libraries ---
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
library(readr)

# --- Step 1: Load AF Risk Loci (Entrez IDs) ---
# Option 1: If you saved it earlier
# entrez_ids <- readRDS("data/AF_Entrez_IDs.rds")

# Option 2: Or load from mapped CSV (ensure column name is Entrez_ID)
AF_genes <- read.csv("data/Cleaned_AF_genes_with_Entrez.csv", stringsAsFactors = FALSE)
entrez_ids <- AF_genes$Entrez_ID %>% as.character() %>% unique() %>% na.omit()

cat("✅ Loaded", length(entrez_ids), "AF Entrez IDs.\n")

# --- Step 2: Load DEG tables ---
deg_files <- list.files("data/DEGs/", pattern = "Toptable_.*\\.csv", full.names = TRUE)
if (length(deg_files) == 0) stop("❌ No DEG files found in data/DEGs/")
deg_list  <- lapply(deg_files, read.csv)
names(deg_list) <- gsub("Toptable_|\\.csv", "", basename(deg_files))

# --- Step 3: Fisher test function ---
fisher_or <- function(df, sample_name) {
  if (!"Entrez_ID" %in% colnames(df)) return(NULL)

  df <- df %>%
    mutate(
      DEG = adj.P.Val < 0.05,
      AF_risk = Entrez_ID %in% entrez_ids
    )

  a <- sum(df$DEG & df$AF_risk, na.rm = TRUE)
  b <- sum(df$DEG & !df$AF_risk, na.rm = TRUE)
  c <- sum(!df$DEG & df$AF_risk, na.rm = TRUE)
  d <- sum(!df$DEG & !df$AF_risk, na.rm = TRUE)

  # Fisher’s exact test
  test <- tryCatch(
    fisher.test(matrix(c(a, b, c, d), nrow = 2)),
    error = function(e) fisher.test(matrix(c(a, b, c, d), nrow = 2), simulate.p.value = TRUE)
  )

  tibble(
    Sample = sample_name,
    DE_Risk = a,
    DE_nonRisk = b,
    nonDE_Risk = c,
    nonDE_nonRisk = d,
    OR = unname(test$estimate),
    Lower_CI = test$conf.int[1],
    Upper_CI = test$conf.int[2],
    Pval = test$p.value,
    Stars = case_when(
      test$p.value < 0.001 ~ "***",
      test$p.value < 0.01  ~ "**",
      test$p.value < 0.05  ~ "*",
      TRUE ~ ""
    )
  )
}

# --- Step 4: Run Fisher tests for all DEG tables ---
results <- bind_rows(mapply(fisher_or, deg_list, names(deg_list), SIMPLIFY = FALSE))

# --- Step 5: Extract metadata (Drug, Conc, Time) ---
results <- results %>%
  separate(Sample, into = c("Drug","Conc","Time"), sep = "_") %>%
  mutate(
    Label = paste(Drug, Conc, sep = "_"),
    Time = factor(Time, levels = c("3","24","48"))
  )

# --- Step 6: Forest plot ---
p <- ggplot(results, aes(x = Label, y = OR, ymin = Lower_CI, ymax = Upper_CI)) +
  geom_pointrange(aes(color = Pval < 0.05), size = 0.9) +
  geom_text(aes(label = Stars), hjust = -0.5, size = 5) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "grey40")) +
  coord_flip() +
  facet_wrap(~Time, ncol = 1, scales = "free_y") +
  ylim(0, 20) +
  labs(
    title = "Atrial Fibrillation Risk Loci Enrichment Across Conditions",
    x = "Condition (Drug_Conc)",
    y = "Odds Ratio (95% CI)"
  ) +
  theme_classic(base_size = 14) +
  theme(
    legend.position = "none",
    strip.text = element_text(face = "bold", size = 12)
  )

# --- Step 7: Display & save ---
print(p)
#ggsave("plots/ForestPlot_AF_RiskLoci.png", plot = p, width = 7, height = 9, dpi = 300)

# --- Step 8: Export raw enrichment data ---
write.csv(results, "data/AF_Cardiotoxicity_ForestPlot_Data.csv", row.names = FALSE)

cat("✅ AF enrichment analysis complete. Results saved to data/AF_Cardiotoxicity_ForestPlot_Data.csv\n")
```

## **📌 Odds Ratios for CorrMotif Groups (AF genes)**

```{r SC_21, echo=TRUE, message=FALSE, fig.height=10,fig.width=12}
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)

# --- Load AF Gene Entrez IDs ---
# Option 1: from mapped CSV
AF_genes <- read.csv("data/Cleaned_AF_genes_with_Entrez.csv", stringsAsFactors = FALSE)
af_entrez <- AF_genes$Entrez_ID %>% as.character() %>% unique() %>% na.omit()

# Option 2: if saved as RDS earlier
# af_entrez <- readRDS("data/AF_Entrez_IDs.rds")

cat("✅ Loaded", length(af_entrez), "AF Entrez IDs.\n")

# --- Load CorrMotif Groups ---
# 0.1 µM
prob_1_0.1 <- as.character(read.csv("data/prob_1_0.1.csv")$Entrez_ID)
prob_2_0.1 <- as.character(read.csv("data/prob_2_0.1.csv")$Entrez_ID)
prob_3_0.1 <- as.character(read.csv("data/prob_3_0.1.csv")$Entrez_ID)

# 0.5 µM
prob_1_0.5 <- as.character(read.csv("data/prob_1_0.5.csv")$Entrez_ID)
prob_2_0.5 <- as.character(read.csv("data/prob_2_0.5.csv")$Entrez_ID)
prob_3_0.5 <- as.character(read.csv("data/prob_3_0.5.csv")$Entrez_ID)
prob_4_0.5 <- as.character(read.csv("data/prob_4_0.5.csv")$Entrez_ID)
prob_5_0.5 <- as.character(read.csv("data/prob_5_0.5.csv")$Entrez_ID)

# --- Annotate Groups ---
df_0.1 <- data.frame(Entrez_ID = unique(c(prob_1_0.1, prob_2_0.1, prob_3_0.1))) %>%
  mutate(
    Response_Group = case_when(
      Entrez_ID %in% prob_1_0.1 ~ "Non response (0.1)",
      Entrez_ID %in% prob_2_0.1 ~ "CX_DOX_1",
      Entrez_ID %in% prob_3_0.1 ~ "DOX_sp_1"
    ),
    Category = ifelse(Entrez_ID %in% af_entrez, "AF Genes", "Non-AF Genes"),
    Concentration = "0.1"
  )

df_0.5 <- data.frame(Entrez_ID = unique(c(prob_1_0.5, prob_2_0.5, prob_3_0.5, prob_4_0.5, prob_5_0.5))) %>%
  mutate(
    Response_Group = case_when(
      Entrez_ID %in% prob_1_0.5 ~ "Non response (0.5)",
      Entrez_ID %in% prob_2_0.5 ~ "DOX_sp_2",
      Entrez_ID %in% prob_3_0.5 ~ "DOX_sp_3",
      Entrez_ID %in% prob_4_0.5 ~ "CX_DOX_2",
      Entrez_ID %in% prob_5_0.5 ~ "CX_DOX_3"
    ),
    Category = ifelse(Entrez_ID %in% af_entrez, "AF Genes", "Non-AF Genes"),
    Concentration = "0.5"
  )

# --- Combine all CorrMotif groups ---
df_combined <- bind_rows(df_0.1, df_0.5)

# --- Fisher Odds Ratio Function ---
fisher_or_group <- function(df_group, df_all, group_name, conc) {
  # counts in group
  a <- sum(df_group$Category == "AF Genes")
  b <- sum(df_group$Category == "Non-AF Genes")

  # counts in rest of groups at same concentration
  ref <- df_all %>% filter(Response_Group != group_name)
  c <- sum(ref$Category == "AF Genes")
  d <- sum(ref$Category == "Non-AF Genes")

  mat <- matrix(c(a, b, c, d), nrow = 2)
  if (any(mat == 0)) mat <- mat + 0.5  # continuity correction

  test <- fisher.test(mat)

  tibble(
    Response_Group = group_name,
    Concentration  = conc,
    a = a, b = b, c = c, d = d,
    OR = unname(test$estimate),
    Lower_CI = test$conf.int[1],
    Upper_CI = test$conf.int[2],
    Pval = test$p.value,
    Stars = case_when(
      test$p.value < 0.001 ~ "***",
      test$p.value < 0.01  ~ "**",
      test$p.value < 0.05  ~ "*",
      TRUE ~ ""
    )
  )
}

# --- Run Fisher tests across groups ---
results <- list()
for (conc in unique(df_combined$Concentration)) {
  conc_df <- df_combined %>% filter(Concentration == conc)
  for (grp in unique(conc_df$Response_Group)) {
    grp_df <- conc_df %>% filter(Response_Group == grp)
    results[[paste(conc, grp)]] <- fisher_or_group(grp_df, conc_df, grp, conc)
  }
}
results <- bind_rows(results)

# --- Save Results ---
write.csv(results, "data/CorrMotif_AFGenes_OddsRatios.csv", row.names = FALSE)
cat("✅ Results saved to data/CorrMotif_AFGenes_OddsRatios.csv\n")

# --- Forest Plot ---
p <- ggplot(results, aes(x = Response_Group, y = OR, ymin = Lower_CI, ymax = Upper_CI)) +
  geom_pointrange(aes(color = Pval < 0.05), size = 0.9) +
  geom_text(aes(label = Stars), hjust = -0.5, size = 5) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "grey40")) +
  coord_flip() +
  facet_wrap(~Concentration, ncol = 1, scales = "free_y") +
  ylim(0, 20) +
  labs(
    title = "AF Gene Enrichment Across CorrMotif Groups",
    x = "Response Group",
    y = "Odds Ratio (95% CI)"
  ) +
  theme_classic(base_size = 14) +
  theme(
    legend.position = "none",
    strip.text = element_text(face = "bold", size = 12)
  )

p
```


## **📌CX-5461 Sensitivity Comparison (All values in µM) Unified naming: LD50 (µM)**
```{r SC_22, echo=TRUE, message=FALSE, fig.height=8,fig.width=10}
library(ggplot2)
library(dplyr)

## === iPSC-CM LD50 (µM) ===
ipsc_vals <- c(6.4, 10.9, 10.0)
ipsc_df <- data.frame(
  CellLine = c("iPSC-CM_1", "iPSC-CM_2", "iPSC-CM_3"),
  LD50 = ipsc_vals,
  Group = "iPSC-CM"
)

## === Sanij et al. (GI50 nM → µM, renamed as LD50) ===
sanij_data <- data.frame(
  CellLine = c("OVCAR3","FUOV1","COLO704","TOV112D","CH1","A2780","RMGI","2008","SKOV3","OVCA432",
               "OAW42","ES2","EFO27","IGROV1","Caov3","Colo720E","MCAS","OVCAR5","OVCAR4","OVCAR8",
               "JHOC5","JHOM1","KURAMOCHI","JHOC7","JHOS3","RMGII","OAW28","OV90"),
  Mean_nM = c(12,25.33,31.5,49.67,73.5,82.33,143,106.7,301.3,206.7,
              226.7,181.3,417,422.3,409.3,413.5,357.6,100.5,613.3,859,
              731,861.2,1082,3267,3177,3370,3850,5170)
) %>%
  dplyr::mutate(
    LD50 = Mean_nM / 1000,  # convert to µM
    Group = ifelse(Mean_nM < 2000, "Sensitive", "Resistant")
  ) %>%
  dplyr::select(CellLine, LD50, Group)

## === Cornelison et al. (IC50 µM, renamed as LD50) ===
cornelison <- data.frame(
  CellLine = c("A2780ip2","A2780cp20","SKOV3ip1","SKOV3TRip2",
               "HeyA8","HeyA8MDR","PEO1","PEO4","OV90","OVCAR3",
               "OAW42","OVSAHO","CAOV3","COV362","ES2","HIO-180"),
  LD50 = c(0.032,0.146,0.595,0.109,
           2.05,0.191,0.525,1.20,1.06,2.00,
           0.300,0.636,0.955,0.645,0.294,5.49),
  Group = c(rep("Sensitive",15),"Resistant")
)

## === Combine all datasets ===
all_data <- dplyr::bind_rows(sanij_data, cornelison, ipsc_df)

## === Plot (linear scale) ===
ggplot(all_data, aes(x = Group, y = LD50, fill = Group)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.6, width = 0.6,
               color = "black", linewidth = 0.4) +
  geom_point(aes(color = Group),
             position = position_nudge(x = 0),
             size = 3, alpha = 0.9, show.legend = FALSE) +
  scale_fill_manual(values = c("Sensitive"="#4A90E2",
                               "Resistant"="#B0B0B0",
                               "iPSC-CM"="#E74C3C")) +
  scale_color_manual(values = c("Sensitive"="#4A90E2",
                                "Resistant"="#B0B0B0",
                                "iPSC-CM"="#E74C3C")) +
  labs(
    title = expression("CX-5461 Sensitivity (LD"[50]*", µM)"),
    x = "",
    y = expression("LD"[50]*" (µM)")
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "right",
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.text = element_text(color = "black")
  )
```

## **📌Elbow plots only — CX-5461 / DOX vs VEH 0.1 & 0.5 µM × 3, 24, 48 h**
```{r SC_23, echo=TRUE, message=FALSE, fig.height=8,fig.width=10}
suppressPackageStartupMessages({
  library(dplyr)
  library(readr)
  library(stringr)
  library(tibble)
  library(tidyr)
})

# ------------------------------------------------------------
# INPUT FILES
# ------------------------------------------------------------
log2cpm_file <- "data/Feature_count_Matrix_Log2CPM_filtered.csv"
meta_file    <- "data/Metadata.csv"

# ------------------------------------------------------------
# LOAD DATA
# ------------------------------------------------------------
log2cpm <- read.csv(log2cpm_file, check.names = FALSE)
colnames(log2cpm) <- gsub("^X", "", trimws(colnames(log2cpm)))

Metadata <- read.csv(meta_file, check.names = FALSE)
Metadata$Sample_name <- gsub("^([0-9]+)\\.([0-9]+)", "\\1-\\2", Metadata$Sample_name)

id_col <- grep("^Entrez|ENTREZ", colnames(log2cpm), value = TRUE)[1]
rownames(log2cpm) <- log2cpm[[id_col]]

# ------------------------------------------------------------
# FUNCTION: plot elbow for one condition
# ------------------------------------------------------------
plot_elbow_one <- function(drug_label = "CX-5461", conc = 0.1, time_h = 3) {
  deg_prefix <- ifelse(drug_label == "CX-5461", "CX", "DOX")
  deg_file <- sprintf("data/DEGs/Toptable_%s_%s_%s.csv", deg_prefix, conc, time_h)

  if (!file.exists(deg_file)) {
    message("Missing DEG file: ", deg_file)
    return()
  }

  deg <- read.csv(deg_file)
  sig <- deg %>% filter(adj.P.Val < 0.05) %>% pull(Entrez_ID) %>% unique()
  if (length(sig) == 0) {
    message("No DEGs in ", deg_file)
    return()
  }

  samples <- Metadata %>%
    filter(Drug %in% c(drug_label, "VEH"),
           Conc. == conc,
           Time == time_h) %>%
    pull(Sample_name)

  matched <- intersect(samples, colnames(log2cpm))
  if (length(matched) == 0) {
    message("No matching samples for ", drug_label, " ", conc, "µM ", time_h, "h")
    return()
  }

  M <- log2cpm[rownames(log2cpm) %in% sig, matched, drop = FALSE]
  M <- as.matrix(M)
  if (nrow(M) < 3) {
    message("Too few genes (<3) for elbow plot: ", drug_label, " ", conc, "µM ", time_h, "h")
    return()
  }

  # ---- K-means elbow ----
  set.seed(123)
  max_k <- min(10, nrow(M) - 1)
  wss <- sapply(1:max_k, function(k)
    kmeans(M, centers = k, nstart = 10, iter.max = 50)$tot.withinss)

  plot(1:max_k, wss, type = "b", pch = 19, col = "darkblue",
       xlab = "Number of Clusters (K)",
       ylab = "Total Within-Cluster SS",
       main = sprintf("Elbow — %s (%.1f µM, %dh) vs VEH", drug_label, conc, time_h))
}

# ------------------------------------------------------------
# EXECUTE — Generate all 12 elbow plots sequentially
# ------------------------------------------------------------

# CX-5461
for (cc in c(0.1, 0.5)) {
  for (tt in c(3, 24, 48)) {
    message(">>> CX-5461 ", cc, " µM ", tt, " h")
    plot_elbow_one("CX-5461", cc, tt)
    dev.flush(); Sys.sleep(1)
  }
}

# DOX
for (cc in c(0.1, 0.5)) {
  for (tt in c(3, 24, 48)) {
    message(">>> DOX ", cc, " µM ", tt, " h")
    plot_elbow_one("DOX", cc, tt)
    dev.flush(); Sys.sleep(1)
  }
}
```

## **📌CX-5461 & DOX vs VEH Heatmaps (0.1 / 0.5 µM ; 3 / 24 / 48 h)**
```{r SC_24, echo=TRUE, message=FALSE, fig.height=8,fig.width=10}
suppressPackageStartupMessages({
  library(ComplexHeatmap)
  library(circlize)
  library(dplyr)
  library(readr)
  library(tibble)
  library(tidyr)
  library(RColorBrewer)
  library(stringr)
})

# ------------------------------------------------------------
# INPUT FILES
# ------------------------------------------------------------
log2cpm_file <- "data/Feature_count_Matrix_Log2CPM_filtered.csv"
meta_file    <- "data/Metadata.csv"

# ------------------------------------------------------------
# LOAD DATA
# ------------------------------------------------------------
log2cpm <- read.csv(log2cpm_file, check.names = FALSE)
colnames(log2cpm) <- gsub("^X", "", trimws(colnames(log2cpm)))

Metadata <- read.csv(meta_file, check.names = FALSE)
Metadata$Sample_name <- gsub("^([0-9]+)\\.([0-9]+)", "\\1-\\2", Metadata$Sample_name)

id_col <- grep("^Entrez|ENTREZ", colnames(log2cpm), value = TRUE)[1]
rownames(log2cpm) <- log2cpm[[id_col]]

# ------------------------------------------------------------
# COLORS & MAPS
# ------------------------------------------------------------
rename_map <- c("17-3"="1","75-1"="2","84-1"="3","90-1"="4","87-1"="5","78-1"="6")
indv_colors <- setNames(brewer.pal(6, "Dark2"), as.character(1:6))
trt_colors  <- c("CX-5461"="#8B006D", "DOX"="#DF707E", "VEH"="#41B333")
conc_colors <- c("0.1"="lightblue", "0.5"="lightcoral")
time_colors <- c("3"="purple", "24"="pink", "48"="tomato3")

cluster_map <- list(
  "CX_0.1_3"=NA, "CX_0.1_24"=3, "CX_0.1_48"=3,
  "CX_0.5_3"=NA, "CX_0.5_24"=3, "CX_0.5_48"=3,
  "DOX_0.1_3"=NA, "DOX_0.1_24"=3, "DOX_0.1_48"=3,
  "DOX_0.5_3"=3,  "DOX_0.5_24"=3, "DOX_0.5_48"=3
)

# ------------------------------------------------------------
# FUNCTION — DRAW AND SHOW HEATMAP
# ------------------------------------------------------------
plot_heatmap_show <- function(drug_label="CX-5461", conc=0.1, time_h=3) {
  deg_prefix <- ifelse(drug_label == "CX-5461", "CX", "DOX")
  deg_file <- sprintf("data/DEGs/Toptable_%s_%s_%s.csv", deg_prefix, conc, time_h)
  key <- sprintf("%s_%s_%s", deg_prefix, conc, time_h)
  row_k <- cluster_map[[key]]

  if (!file.exists(deg_file)) {
    message("❌ Missing DEG file: ", deg_file)
    return()
  }

  deg <- read.csv(deg_file)
  sig <- deg %>% filter(adj.P.Val < 0.05) %>% pull(Entrez_ID) %>% unique()
  if (length(sig) == 0) {
    message("⚠️ No DEGs for ", key)
    return()
  }

  samples <- Metadata %>%
    filter(Drug %in% c(drug_label,"VEH"),
           Conc. == conc,
           Time == time_h) %>%
    pull(Sample_name)

  matched <- intersect(samples, colnames(log2cpm))
  if (length(matched) == 0) {
    message("⚠️ No matching samples for ", key)
    return()
  }

  M <- log2cpm[rownames(log2cpm) %in% sig, matched, drop=FALSE]
  if (nrow(M) == 0) {
    message("⚠️ Empty matrix for ", key)
    return()
  }

  M <- as.matrix(M)
  colnames(M) <- str_replace_all(colnames(M), rename_map)

  # --- Annotation
  annot_df <- tibble(timeset = colnames(M)) %>%
    mutate(sample = timeset) %>%
    separate(timeset, into=c("indv","trt","conc","time"), sep="_", remove=FALSE) %>%
    mutate(trt=factor(trt,levels=c(drug_label,"VEH")),
           indv=factor(indv,levels=as.character(1:6)),
           conc=factor(conc,levels=c("0.1","0.5")),
           time=factor(time,levels=c("3","24","48"))) %>%
    column_to_rownames("sample")

  top_ha <- HeatmapAnnotation(
    df=annot_df[,c("trt","indv","time")],
    col=list(trt=trt_colors, indv=indv_colors, time=time_colors)
  )

  # --- Color scale
  q <- quantile(as.numeric(M), c(0.01, 0.5, 0.99), na.rm=TRUE)
  col_fun <- colorRamp2(c(q[1], q[2], q[3]), c("blue","white","red"))

  # --- Plotting
  message("✅ Displaying: ", key,
          ifelse(is.na(row_k), " (no clusters)", paste0(" (k=", row_k, ")")))

  if (is.na(row_k)) {
    ht <- Heatmap(
      M,
      top_annotation=top_ha,
      show_column_names=TRUE,
      show_row_names=FALSE,
      cluster_columns=TRUE,
      cluster_rows=FALSE,
      col=col_fun,
      use_raster=TRUE,
      raster_device="png",
      raster_quality=2,
      column_title=sprintf("%s (%.1f µM ; %dh) vs VEH — log2CPM",
                           drug_label, conc, time_h),
      row_title=NULL
    )
  } else {
    ht <- Heatmap(
      M,
      top_annotation=top_ha,
      show_column_names=TRUE,
      show_row_names=FALSE,
      cluster_columns=TRUE,
      cluster_rows=FALSE,
      row_km=row_k,
      col=col_fun,
      use_raster=TRUE,
      raster_device="png",
      raster_quality=2,
      column_title=sprintf("%s (%.1f µM ; %dh) vs VEH — log2CPM",
                           drug_label, conc, time_h),
      row_title="Cluster"
    )
  }

  draw(ht)
}

# ------------------------------------------------------------
# RUN ALL COMBOS
# ------------------------------------------------------------
for (drug in c("CX-5461","DOX")) {
  for (cc in c(0.1,0.5)) {
    for (tt in c(3,24,48)) {
      message("\n>>> ", drug, " ", cc, " µM ", tt, " h")
      plot_heatmap_show(drug, cc, tt)
    }
  }
}

message("\n🎨 All heatmaps displayed sequentially.")
```
